### 2019-06-22 example.tex
Added all caps first sentence and large drop-cap first letter (lettrine package)

\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode]{dndbook}

% Use babel or polyglossia to automatically redefine macros for terms
% Armor Class, Level, etc...
% Default output is in English; captions are located in lib/dndstrings.sty.
% If no captions exist for a language, English will be used.
%1. To load a language with babel:
%	\usepackage[<lang>]{babel}
%2. To load a language with polyglossia:
%	\usepackage{polyglossia}
%	\setdefaultlanguage{<lang>}
\usepackage[english]{babel}
%\usepackage[italian]{babel}
% For further options (multilanguage documents, hypenations, language environments...)
% please refer to babel/polyglossia's documentation.

\usepackage[utf8]{inputenc}
\usepackage[singlelinecheck=false]{caption}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{shortvrb}
\usepackage{stfloats}
\usepackage{lmodern} % Scalable font
\usepackage{lettrine} % For the drop cap

\captionsetup[table]{labelformat=empty,font={sf,sc,bf,},skip=0pt}

\MakeShortVerb{|}

\lstset{%
  basicstyle=\ttfamily,
  language=[LaTeX]{TeX},
  breaklines=true,
}

\title{The Dark \LaTeX{} \\
\large An Example of the dndbook Class}
\author{The rpgTeX Team}
\date{2020/04/21}

\begin{document}

\frontmatter

\maketitle

\tableofcontents

\mainmatter%

\part{Layout}

\chapter{Sections}

\DndDropCapLine{T}{his package is designed to aid you in} writing beautifully typeset documents for the fifth edition of the world's greatest roleplaying game. It starts by adjusting the section formatting from the defaults in \LaTeX{} to something a bit more familiar to the reader. The chapter formatting is displayed above.

\section{Section}
Sections break up chapters into large groups of associated text.

\subsection{Subsection}
Subsections further break down the information for the reader.

\subsubsection{Subsubsection}
Subsubsections are the furthest division of text that still have a block header. Below this level, headers are displayed inline.

\paragraph{Paragraph}
The paragraph format is seldom used in the core books, but is available if you prefer it to the ``normal'' style.

\subparagraph{Subparagraph}
The subparagraph format with the paragraph indent is likely going to be more familiar to the reader.

\section{Special Sections}
The module also includes functions to aid in the proper typesetting of multi-line section headers: |\DndFeatHeader| for feats, |\DndItemHeader| magic items and traps, and |\DndSpellHeader| for spells.

\DndFeatHeader{Typesetting Savant}[Prerequisite: \LaTeX{} distribution]
You have acquired a package which aids in typesetting source material for one of your favorite games, giving you the following benefits:

\begin{itemize}
  \item You have advantage on Intelligence checks to typeset new content.
  \item When you fail an Intelligence check to typeset new content, you can ask questions online at the package's website.
\end{itemize}

\DndItemHeader{Foo's Quill}{Wondrous item, rare}
This quill has 3 charges. While holding it, you can use an action to expend 1 of its charges. The quill leaps from your hand and writes a contract applicable to your situation.

The quill regains 1d3 expended charges daily at dawn.

\DndSpellHeader%
  {Beautiful Typesetting}
  {4th-level illusion}
  {1 action}
  {5 feet}
  {S, M (ink and parchment, which the spell consumes)}
  {Until dispelled}
You are able to transform a written message of any length into a beautiful scroll. All creatures within range that can see the scroll must make a wisdom saving throw or be charmed by you until the spell ends.

While the creature is charmed by you, they cannot take their eyes off the scroll and cannot willingly move away from the scroll. Also, the targets can make a wisdom saving throw at the end of each of their turns. On a success, they are no longer charmed.

\section{Map Regions}
The map region functions |\DndArea| and |\DndSubArea| provide automatic numbering of areas.

\DndArea{Village of Hommlet}
This is the village of hommlet.

\DndSubArea{Inn of the Welcome Wench}
Inside the village is the inn of the Welcome Wench.

\DndSubArea{Blacksmith's Forge}
There's a blacksmith in town, too.

\DndArea{Foo's Castle}
This is foo's home, a hovel of mud and sticks.

\DndSubArea{Moat}
This ditch has a board spanning it.

\DndSubArea{Entrance}
A five-foot hole reveals the dirt floor illuminated by a hole in the roof.

\chapter{Text Boxes}

The module has three environments for setting text apart so that it is drawn to the reader's attention. |DndReadAloud| is used for text that a game master would read aloud.

\begin{DndReadAloud}
  As you approach this module you get a sense that the blood and tears of many generations went into its making. A warm feeling welcomes you as you type your first words.
\end{DndReadAloud}

\section{As an Aside}
The other two environments are the |DndComment| and the |DndSidebar|. The |DndComment| is breakable and can safely be used inline in the text.

\begin{DndComment}{This Is a Comment Box!}
  A |DndComment| is a box for minimal highlighting of text. It lacks the ornamentation of |DndSidebar|, but it can handle being broken over a column.
\end{DndComment}

The |DndSidebar| is not breakable and is best used floated toward a page corner as it is below.

\begin{DndSidebar}[float=!b]{Behold the DndSidebar!}
  The |DndSidebar| is used as a sidebar. It does not break over columns and is best used with a figure environment to float it to one corner of the page where the surrounding text can then flow around it.
\end{DndSidebar}

\section{Tables}
The |DndTable| colors the even rows and is set to the width of a line by default.

\begin{DndTable}[header=Nice Table]{XX}
    Table head  & Table head \\
    Some value  & Some value \\
    Some value  & Some value \\
    Some value  & Some value
\end{DndTable}

\chapter{Monsters and NPCs}

% Monster stat block
\begin{DndMonster}[float*=b,width=\textwidth + 8pt]{Monster Foo}
  \begin{multicols}{2}
    \DndMonsterType{Medium aberration (metasyntactic variable), neutral evil}

    % If you want to use commas in the key values, enclose the values in braces.
    \DndMonsterBasics[
        armor-class = {9 (12 with \emph{mage armor})},
        hit-points  = {\DndDice{3d8 + 3}},
        speed       = {30 ft., fly 30 ft.},
      ]

    \DndMonsterAbilityScores[
        str = 12,
        dex = 8,
        con = 13,
        int = 10,
        wis = 14,
        cha = 15,
      ]

    \DndMonsterDetails[
        %saving-throws = {Str +0, Dex +0, Con +0, Int +0, Wis +0, Cha +0},
        %skills = {Acrobatics +0, Animal Handling +0, Arcana +0, Athletics +0, Deception +0, History +0, Insight +0, Intimidation +0, Investigation +0, Medicine +0, Nature +0, Perception +0, Performance +0, Persuasion +0, Religion +0, Sleight of Hand +0, Stealth +0, Survival +0},
        %damage-vulnerabilities = {cold},
        %damage-resistances = {bludgeoning, piercing, and slashing from nonmagical attacks},
        %damage-immunities = {poison},
        %condition-immunities = {poisoned},
        senses = {darkvision 60 ft., passive Perception 10},
        languages = {Common, Goblin, Undercommon},
        challenge = 1,
      ]
    % Traits
    \DndMonsterAction{Innate Spellcasting}
    Foo's spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It can innately cast the following spells, requiring no material components:
    \begin{DndMonsterSpells}
      \DndInnateSpellLevel{misty step}
      \DndInnateSpellLevel[3]{fog cloud, rope trick}
      \DndInnateSpellLevel[1]{identify}
    \end{DndMonsterSpells}

    \DndMonsterAction{Spellcasting}
    Foo is a 2nd-level spellcaster. Its spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It has the following sorcerer spells prepared:
    \begin{DndMonsterSpells}
      \DndMonsterSpellLevel{blade ward, fire bolt, light, shocking grasp}
      \DndMonsterSpellLevel[1][3]{burning hands, mage armor, shield}
    \end{DndMonsterSpells}

    \DndMonsterSection{Actions}
    \DndMonsterAction{Multiattack}
    The foo makes two melee attacks.

    %Default values are shown commented out
    \DndMonsterAttack[
      name=Dagger,
      %distance=both, % valid options are in the set {both,melee,ranged},
      %type=weapon, %valid options are in the set {weapon,spell}
      mod=+3,
      %reach=5,
      %range=20/60,
      %targets=one target,
      dmg=\DndDice{1d4+1},
      dmg-type=piercing,
      %plus-dmg=,
      %plus-dmg-type=,
      %or-dmg=,
      %or-dmg-when=,
      %extra=,
    ]

    %\DndMonsterMelee calls \DndMonsterAttack with the melee option
    \DndMonsterMelee[
      name=Flame Tongue Longsword,
      mod=+3,
      %reach=5,
      %targets=one target,
      dmg=\DndDice{1d8+1},
      dmg-type=slashing,
      plus-dmg=\DndDice{2d6},
      plus-dmg-type=fire,
      or-dmg=\DndDice{1d10+1},
      or-dmg-when=if used with two hands,
      %extra=,
    ]

    %\DndMonsterRanged calls \DndMonsterAttack with the ranged option
    \DndMonsterRanged[
      name=Assassin's Light Crossbow,
      mod=+1,
      range=80/320,
      dmg=\DndDice{1d8},
      dmg-type=piercing,
      %plus-dmg=,
      %plus-dmg-type=,
      %or-dmg=,
      %or-dmg-when=,
      extra={, and the target must make a DC 15 Constitution saving throw, taking 24 (7d6) poison damage on a failed save, or half as much damage on a successful one}
    ]

    % Legendary Actions
    \DndMonsterSection{Legendary Actions}
    The foo can take 3 legendary actions, choosing from the options below. Only one legendary action option can be used at a time and only at the end of another creature's turn. The foo regains spent legendary actions at the start of its turn.

    \begin{DndMonsterLegendaryActions}
      \DndMonsterLegendaryAction{Move}{The foo moves up to its speed.}
      \DndMonsterLegendaryAction{Dagger Attack}{The foo makes a dagger attack.}
      \DndMonsterLegendaryAction{Create Contract (Costs 3 Actions)}{The foo presents a contract in a language it knows and waves it in the face of a creature within 10 feet. The creature must make a DC 10 Intelligence saving throw. On a failure, the creature is incapacitated until the start of the foo's next turn. A creature who cannot read the language in which the contract is written has advantage on this saving throw.}
    \end{DndMonsterLegendaryActions}
  \end{multicols}
\end{DndMonster}

The |DndMonster| environment is used to typeset monster and NPC stat blocks. The module supplies many functions to easily typeset the contents of the stat block

\part{Customization}

\chapter{Colors}

\begin{table*}[b]
  \caption{\DndFontTableTitle{}Colors Supported by this Package}\label{tab:colors}

  \begin{tabularx}{\linewidth}{lX}
    \textbf{Color}                  & \textbf{Description} \\
    \rowcolor{PhbLightGreen}
    |PhbLightGreen|                 & Light green used in PHB Part 1 (Default) \\
    \rowcolor{PhbLightCyan}
    |PhbLightCyan|                  & Light cyan used in PHB Part 2 \\
    \rowcolor{PhbMauve}
    |PhbMauve|                      & Pale purple used in PHB Part 3 \\
    \rowcolor{PhbTan}
    |PhbTan|                        & Light brown used in PHB appendix \\
    \rowcolor{DmgLavender}
    |DmgLavender|                   & Pale purple used in DMG Part 1 \\
    \rowcolor{DmgCoral}
    |DmgCoral|                      & Orange-pink used in DMG Part 2 \\
    \rowcolor{DmgSlateGray}
    |DmgSlateGray| (|DmgSlateGrey|) & Blue-gray used in PHB Part 3 \\
    \rowcolor{DmgLilac}
    |DmgLilac|                      & Purple-gray used in DMG appendix \\
    \rowcolor{BrGreen}
    |BrGreen|                       & Gray-green used for tables in Basic Rules\\
  \end{tabularx}
\end{table*}

This package provides several global color variables to style |DndComment|, |DndReadAloud|, |DndSidebar|, and |DndTable| environments.

\begin{DndTable}[header=Box Colors]{lX}
  Color            &  Description \\
  |commentcolor|   & |DndComment| background \\
  |readaloudcolor| & |DndReadAloud| background \\
  |sidebarcolor|   & |DndSidebar| background \\
  |tablecolor|     & background of even |DndTable| rows \\
\end{DndTable}

They also accept an optional color argument to set the color for a single instance. See Table~\ref{tab:colors} for a list of core book accent colors.

\begin{lstlisting}
\begin{DndTable}[color=PhbLightCyan]{cX}
  d8 & Item \\
  1  & Small wooden button \\
  2  & Red feather \\
  3  & Human tooth \\
  4  & Vial of green liquid \\
  5  & Loaded dice \\
  6  & Tasty biscuit \\
  7  & Broken axe handle \\
  8  & Tarnished silver locket \\
\end{DndTable}
\end{lstlisting}

\begin{DndTable}[color=PhbLightCyan]{cX}
  d8 & Item \\
  1  & Small wooden button \\
  2  & Red feather \\
  3  & Human tooth \\
  4  & Vial of green liquid \\
  5  & Loaded dice \\
  6  & Tasty biscuit \\
  7  & Broken axe handle \\
  8  & Tarnished silver locket \\
\end{DndTable}

\section{Themed Colors}
Use |\DndSetThemeColor[<color>]| to set |commentcolor|, |readaloudcolor|, |sidebarcolor|, and |tablecolor| to a specific color. Calling |\DndSetThemeColor| without an argument sets those colors to the current |themecolor|. In the following example the group limits the change to just a few boxes; after the group finishes, the colors are reverted to what they were before the group started.

\begin{lstlisting}
\begingroup
\DndSetThemeColor[PhbMauve]

\begin{DndComment}{This Comment Is in Mauve}
  This comment is in the the new color.
\end{DndComment}

\begin{DndSidebar}{This Sidebar Is Also Mauve}
  The sidebar is also using the new theme color.
\end{DndSidebar}
\endgroup
\end{lstlisting}

\begingroup
\DndSetThemeColor[PhbMauve]

\begin{DndComment}{This Comment Is in Mauve}
  This comment is in the the new color.
\end{DndComment}

\begin{DndSidebar}{This Sidebar Is Also Mauve}
  The sidebar is also using the new theme color.
\end{DndSidebar}
\endgroup

\end{document}

### 2019-12-27 example.tex
Added a variable that can override the image used for the background "paper"

@@
-\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode]{dndbook}
+\documentclass[letterpaper,twocolumn,openany]{dndbook}
 
@@
 % Armor Class, Level, etc...
-% Default output is in English; captions are located in lib/dndstrings.sty.
+% Default output is in English; captions are located in lib/dndstring-captions.sty.
 % If no captions exist for a language, English will be used.
@@
 \usepackage{stfloats}
-\usepackage{lmodern} % Scalable font
-\usepackage{lettrine} % For the drop cap
 
 \captionsetup[table]{labelformat=empty,font={sf,sc,bf,},skip=0pt}
+
+% Set the default background paper-like image. This options allows it to be overridden.
+\paperimage{img/paper}
 
@@
 \author{The rpgTeX Team}
-\date{2020/04/21}
+\date{2019/07/18}
 
@@
 \mainmatter%
-
-\part{Layout}
 
@@
 \paragraph{Paragraph}
-The paragraph format is seldom used in the core books, but is available if you prefer it to the ``normal'' style.
+The paragraph format is seldom used in the core books, but is available if you prefer the other style.
 
@@
 
-\section{Special Sections}
-The module also includes functions to aid in the proper typesetting of multi-line section headers: |\DndFeatHeader| for feats, |\DndItemHeader| magic items and traps, and |\DndSpellHeader| for spells.
-
-\DndFeatHeader{Typesetting Savant}[Prerequisite: \LaTeX{} distribution]
-You have acquired a package which aids in typesetting source material for one of your favorite games, giving you the following benefits:
-
-\begin{itemize}
-  \item You have advantage on Intelligence checks to typeset new content.
-  \item When you fail an Intelligence check to typeset new content, you can ask questions online at the package's website.
-\end{itemize}
+\section{Items and Spells}
+The module also includes the functions |\DndItemHeader| and |\DndSpellHeader| to aid in the proper typesetting of items (including magic items and traps) and spells.
 
@@
 \section{Map Regions}
-The map region functions |\DndArea| and |\DndSubArea| provide automatic numbering of areas.
+The map region functions |\area| and |\subarea| provide automatic numbering of areas.
 
@@
 \begin{DndTable}[header=Nice Table]{XX}
-    Table head  & Table head \\
+    \textbf{Table head}  & \textbf{Table head} \\
     Some value  & Some value \\
@@
 
-\part{Customization}
-
 \chapter{Colors}
 
-\begin{table*}[b]
-  \caption{\DndFontTableTitle{}Colors Supported by this Package}\label{tab:colors}
+\begin{table*}[b]%
+  \caption{}\label{tab:colors}
 
-  \begin{tabularx}{\linewidth}{lX}
+  \begin{DndTable}[width=\linewidth,header=Colors Supported by This Package]{lX}
     \textbf{Color}                  & \textbf{Description} \\
-    \rowcolor{PhbLightGreen}
     |PhbLightGreen|                 & Light green used in PHB Part 1 (Default) \\
-    \rowcolor{PhbLightCyan}
     |PhbLightCyan|                  & Light cyan used in PHB Part 2 \\
-    \rowcolor{PhbMauve}
     |PhbMauve|                      & Pale purple used in PHB Part 3 \\
-    \rowcolor{PhbTan}
     |PhbTan|                        & Light brown used in PHB appendix \\
-    \rowcolor{DmgLavender}
     |DmgLavender|                   & Pale purple used in DMG Part 1 \\
-    \rowcolor{DmgCoral}
     |DmgCoral|                      & Orange-pink used in DMG Part 2 \\
-    \rowcolor{DmgSlateGray}
     |DmgSlateGray| (|DmgSlateGrey|) & Blue-gray used in PHB Part 3 \\
-    \rowcolor{DmgLilac}
     |DmgLilac|                      & Purple-gray used in DMG appendix \\
-    \rowcolor{BrGreen}
-    |BrGreen|                       & Gray-green used for tables in Basic Rules\\
-  \end{tabularx}
+  \end{DndTable}
 \end{table*}
@@
 \begin{DndTable}[header=Box Colors]{lX}
-  Color            &  Description \\
+  \textbf{Color}   & \textbf{Description} \\
   |commentcolor|   & |DndComment| background \\
@@
 \begin{lstlisting}
-\begin{DndTable}[color=PhbLightCyan]{cX}
-  d8 & Item \\
+\begin{DndTable}[cX][PhbLightCyan]
+  \textbf{d8} & \textbf{Item} \\
   1           & Small wooden button \\
@@
   4           & Vial of green liquid \\
-  5  & Loaded dice \\
   6           & Tasty biscuit \\
@@
 \begin{DndTable}[color=PhbLightCyan]{cX}
-  d8 & Item \\
+  \textbf{d8} & \textbf{Item} \\
   1           & Small wooden button \\
@@
 \end{DndSidebar}
+
 \endgroup

### 2019-12-27 article.tex
Added an "article" class and example to create small adventure document (unlike the book, no title page or table of contents)

--- 2019-12-27 example.tex
@@
-\documentclass[letterpaper,twocolumn,openany]{dndbook}
+\documentclass[letterpaper,twocolumn,openany]{dndarticle}
 
@@
 \usepackage{stfloats}
+\usepackage{graphicx}
+\usepackage{titling}
 
 \captionsetup[table]{labelformat=empty,font={sf,sc,bf,},skip=0pt}
+\DndSetThemeColor[DmgLavender]
 
-% Set the default background paper-like image. This options allows it to be overridden.
-\paperimage{img/paper}
+% Override the default background "paper" image with an alternate one.
+\paperimage{img/paper-article}
 
@@
 
-\title{The Dark \LaTeX{} \\
-\large An Example of the dndbook Class}
-\author{The rpgTeX Team}
-\date{2019/07/18}
+\font\quipfont=cmr7 at 8pt
+\title{An Authoritative Adventure}
+\author{@author}
+\date{{\quipfont \small\textit{A short quip that describes the adventure, such as ``Who will survive the attack of the murder-hobos?''}}}
+
+% Adds an article image at the top of column 1 above the title, similar to the
+% "Dungeon"-style article. Comment out the below to remove the image.
+\pretitle{
+  \Huge
+  \vspace{-30pt} % Align top of image with column 2.
+  \centering{\includegraphics[width=7cm,height=7cm]{img/title.jpg}\\[\bigskipamount]}
+  \begin{center}
+}
+\posttitle{\end{center}}
 
@@
 
-\frontmatter
-
 \maketitle
-
-\tableofcontents
-
-\mainmatter%
-
-\chapter{Sections}
 
@@
 It starts by adjusting the section formatting from the defaults in \LaTeX{} to something a bit more familiar to the reader.
-The chapter formatting is displayed above.
+The article formatting is displayed above.
+
+The default title layout is reminiscent of the article format in publications such as Dungeon magazine.
 
@@
 
-\chapter{Text Boxes}
+\section{Text Boxes}
 
@@
 
-\section{As an Aside}
+\subsection{As an Aside}
 The other two environments are the |DndComment| and the |DndSidebar|. The |DndComment| is breakable and can safely be used inline in the text.
@@
 
-\section{Tables}
+\subsection{Tables}
 The |DndTable| colors the even rows and is set to the width of a line by default.
@@
 
-\chapter{Monsters and NPCs}
+\section{Monsters and NPCs}
 
@@
 
-\chapter{Colors}
+\section{Colors}
 
@@
 
-\section{Themed Colors}
+\subsection{Themed Colors}
 Use |\DndSetThemeColor[<color>]| to set |commentcolor|, |readaloudcolor|, |sidebarcolor|, and |tablecolor| to a specific color.

### 2020-01-05 article.tex
Added a map style option to prefix numbers with a designated character (or string)

@@
 A five-foot hole reveals the dirt floor illuminated by a hole in the roof.
+
+\section{Alternate Map Region Styles}
+Published modules sometimes use plain numbers for locations, sometimes they
+prefix a character to the front of the numbers. The following options can be
+used to display in these forms:
+
+\numberedarea{Numbered Dungeon}
+Areas in the Numbered Dungeon have sequential numbers. This is done using
+the following commands:
+
+\begin{verbatim}
+\numberedarea{Numbered Dungeon}
+\numberedsubarea{Entry}
+\numberedsubarea{Trap}
+\numberedsubarea{Fight}
+\numberedsubarea{Exit}
+\end{verbatim}
+
+\numberedsubarea{Entry}
+\numberedsubarea{Trap}
+\numberedsubarea{Fight}
+\numberedsubarea{Exit}
+
+\prefixedarea{Ace Dungeon}{A}
+Areas in the Ace Dungeon are prefixed with `\prefixedareaprefix'.
+This is done using the following commands:
+
+\begin{verbatim}
+\prefixedarea{Ace Dungeon}{A}
+\prefixedsubarea{Entry}
+\prefixedsubarea{Exit}
+\end{verbatim}
+
+\prefixedsubarea{Entry}
+\prefixedsubarea{Exit}
+
+\prefixedarea{The Fantastic Zoo}{Z}
+Areas in the Fantastic Zoo are prefixed with `\prefixedareaprefix'.
+
+\prefixedsubarea{Entry}
+\prefixedsubarea{Exit}
 

### 2020-01-17 example.tex
Fixed up the background "paper image" option so that it defaults to the standard one without having to be explicitly defined in the document

@@
-\documentclass[letterpaper,twocolumn,openany]{dndbook}
+\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode]{dndbook}
 
@@
 
-% Set the default background paper-like image. This options allows it to be overridden.
-\paperimage{img/paper}
+% Uncomment to allow the default background paper image to be overridden.
+%\SetPaperImage{img/paper}
 
@@
 \paragraph{Paragraph}
-The paragraph format is seldom used in the core books, but is available if you prefer the other style.
+The paragraph format is seldom used in the core books, but is available if you prefer it to the ``normal'' style.
 
@@
 \section{Map Regions}
-The map region functions |\area| and |\subarea| provide automatic numbering of areas.
+The map region functions |\DndArea| and |\DndSubArea| provide automatic numbering of areas.
 
@@
 \begin{lstlisting}
-\begin{DndTable}[cX][PhbLightCyan]
+\begin{DndTable}[color=PhbLightCyan]{cX}
   \textbf{d8} & \textbf{Item} \\
@@
 \end{DndSidebar}
-
 \endgroup

### 2020-01-18 example.tex

@@
 
-\section{Items and Spells}
-The module also includes the functions |\DndItemHeader| and |\DndSpellHeader| to aid in the proper typesetting of items (including magic items and traps) and spells.
+\section{Special Sections}
+The module also includes functions to aid in the proper typesetting of multi-line section headers: |\DndFeatHeader| for feats, |\DndItemHeader| magic items and traps, and |\DndSpellHeader| for spells.
+
+\DndFeatHeader{Typesetting Savant}[Prerequisite: \LaTeX{} distribution]
+You have acquired a package which aids in typesetting source material for one of your favorite games.
+You have advantage on Intelligence checks to typeset new content.
+On a failed check, you can ask questions online at the package's website.
 

### 2020-04-18 example.tex

@@
 % Armor Class, Level, etc...
-% Default output is in English; captions are located in lib/dndstring-captions.sty.
+% Default output is in English; captions are located in lib/dndstrings.sty.
 % If no captions exist for a language, English will be used.
@@
 
+\part{Layout}
+
 \chapter{Sections}
@@
 \DndFeatHeader{Typesetting Savant}[Prerequisite: \LaTeX{} distribution]
-You have acquired a package which aids in typesetting source material for one of your favorite games.
-You have advantage on Intelligence checks to typeset new content.
-On a failed check, you can ask questions online at the package's website.
+You have acquired a package which aids in typesetting source material for one of your favorite games, giving you the following benefits:
+
+\begin{itemize}
+  \item You have advantage on Intelligence checks to typeset new content.
+  \item When you fail an Intelligence check to typeset new content, you can ask questions online at the package's website.
+\end{itemize}
 
@@
 
+\part{Customization}
+
 \chapter{Colors}
 
-\begin{table*}[b]%
-  \caption{}\label{tab:colors}
+\begin{table*}[b]
+  \caption{\DndFontTableTitle{}Colors Supported by this Package\label{tab:colors}}
 
-  \begin{DndTable}[width=\linewidth,header=Colors Supported by This Package]{lX}
+  \begin{tabularx}{\linewidth}{lX}
     \textbf{Color}                  & \textbf{Description} \\
+    \rowcolor{PhbLightGreen}
     |PhbLightGreen|                 & Light green used in PHB Part 1 (Default) \\
+    \rowcolor{PhbLightCyan}
     |PhbLightCyan|                  & Light cyan used in PHB Part 2 \\
+    \rowcolor{PhbMauve}
     |PhbMauve|                      & Pale purple used in PHB Part 3 \\
+    \rowcolor{PhbTan}
     |PhbTan|                        & Light brown used in PHB appendix \\
+    \rowcolor{DmgLavender}
     |DmgLavender|                   & Pale purple used in DMG Part 1 \\
+    \rowcolor{DmgCoral}
     |DmgCoral|                      & Orange-pink used in DMG Part 2 \\
+    \rowcolor{DmgSlateGray}
     |DmgSlateGray| (|DmgSlateGrey|) & Blue-gray used in PHB Part 3 \\
+    \rowcolor{DmgLilac}
     |DmgLilac|                      & Purple-gray used in DMG appendix \\
-  \end{DndTable}
+    \rowcolor{BrGreen}
+    |BrGreen|                       & Gray-green used for tables in Basic Rules\\
+  \end{tabularx}
 \end{table*}

### 2020-07-26 article.tex
Fixed up the background "paper image" option so that it defaults to the standard one without having to be explicitly defined in the document
Added the "ornamentedbox" and table environment for doing tables like "spellcaster". Attempted adaptation from https://tex.stackexchange.com/a/501736/2575, can't move everything to the dndtable.sty file due to pgfkeys errors with the textcolorbox skin defs.

@@
 \usepackage{titling}
+\usetikzlibrary{intersections}
 
@@
 % Override the default background "paper" image with an alternate one.
-\paperimage{img/paper-article}
+\SetPaperImage{img/paper-article}
 
@@
 \posttitle{\end{center}}
+
+% Code from Loop Space: <https://tex.stackexchange.com/a/26386/73317>
+\makeatletter
+\tikzset{
+  use path for main/.code={%
+    \tikz@addmode{%
+      \expandafter\pgfsyssoftpath@setcurrentpath\csname tikz@intersect@path@name@#1\endcsname
+    }%
+  },
+  use path for actions/.code={%
+    \expandafter\def\expandafter\tikz@preactions\expandafter{\tikz@preactions\expandafter\let\expandafter\tikz@actions@path\csname tikz@intersect@path@name@#1\endcsname}%
+  },
+  use path/.style={%
+    use path for main=#1,
+    use path for actions=#1,
+  }
+}
+\makeatother
+% End of the code from Loop Space
+
+% Ornamented box content from: https://tex.stackexchange.com/a/501736/2575
+% TODO: Work out how to get the rest of the content from here into the dndtable.sty
+%       file, which causes errors like:
+%         ! Package pgfkeys Error: I do not know the key '/tcb/skinfirst'
+\tikzset{ornamented frame inner/.style={color=ornamentedFrameInner,
+                                        line width=2pt},
+         ornamented frame outer/.style={color=ornamentedFrameOuter,
+                                        line width=3pt}}
+
+\tcbsubskin{ornamented}{empty}{
+  skin first=ornamented, skin middle=ornamented, skin last=ornamented,
+  title engine=standard,
+  frame code={
+    % Account for the line widths in order not to draw beyond the bounding
+    % box---except for a few very small details for which this is intentional.
+    \coordinate (north west) at ([shift={(-1.5pt,9.5pt)}]frame.north west);
+    \coordinate (north east) at ([shift={(1.5pt,9.5pt)}]frame.north east);
+    \coordinate (south east) at ([shift={(1.5pt,-9.5pt)}]frame.south east);
+    \coordinate (south west) at ([shift={(-1.5pt,-9.5pt)}]frame.south west);
+    %
+    \foreach \xoffset/\point in {34pt/north west, -34pt/north east,
+                                  34pt/south west, -34pt/south east} {
+      \fill[color=ornamentedFrameOuter]
+        ([xshift=\xoffset]\point) circle[radius=2.5pt];
+    }
+    %
+    \path[name path=ornament 1]  ([yshift=-4pt]north west)
+      [rounded corners=0.5pt] -- ++(23pt,0)
+      [rounded corners=2pt]   -- ++(3pt,-4pt)
+                              -- ([shift={(-26pt,-8pt)}]north east)
+      [rounded corners=0.5pt] -- ++(3pt,4pt)
+      [rounded corners=4pt]   -- ([yshift=-4pt]north east)
+                              -- ([yshift=4pt]south east)
+      [rounded corners=0.5pt] -- ++(-23pt,0)
+      [rounded corners=2pt]   -- ++(-3pt,4pt)
+                              -- ([shift={(26pt,8pt)}]south west)
+      [rounded corners=0.5pt] -- ++(-3pt,-4pt)
+      [rounded corners=4pt]   -- ([yshift=4pt]south west)
+                              -- cycle;
+    %
+    \path[rounded corners=0.5pt, name path=ornament 2]
+                                 ([yshift=-20pt]north west)
+                              -- ++(-4pt,3pt)
+                              -- ++(0,4pt)
+               to[out=0, in=-90] ([shift={(8pt,0pt)}]north west)
+                              -- ([shift={(34pt,0pt)}]north west)
+                              -- ([shift={(-8pt,0pt)}]north east)
+             to[out=-90, in=180] ([shift={(4pt,-13pt)}]north east)
+                              -- ++(0,-4pt)
+                              -- ++(-4pt,-3pt)
+                              -- ([yshift=20pt]south east)
+                              -- ++(4pt,-3pt)
+                              -- ++(0,-4pt)
+              to[out=180, in=90] ([shift={(-8pt,0pt)}]south east)
+                              -- ([shift={(8pt,0pt)}]south west)
+                to[out=90, in=0] ([shift={(-4pt,13pt)}]south west)
+                              -- ++(0,4pt)
+                              -- ++(4pt,3pt)
+                              -- cycle;
+    %
+    \draw[ornamented frame outer, use path=ornament 1,fill=white];
+    \draw[ornamented frame outer, use path=ornament 2];
+    \draw[ornamented frame inner, use path=ornament 1];
+    \draw[ornamented frame inner, use path=ornament 2];
+    %
+    \foreach \xoffset/\point in {34pt/north west, -34pt/north east,
+                                 34pt/south west, -34pt/south east} {
+      \fill[color=ornamentedFrameInner]
+        ([xshift=\xoffset]\point) circle[radius=2pt];
+    }
+  }
+}
+
+% These parameters---especially those related to geometry---are better located
+% here in a style than in the subskin definition (see the Subskins section of
+% the tcolorbox manual).
+\tcbset{ornamented/.style={skin=ornamented, coltitle=black, toptitle=5pt,
+                           % Reserve vertical space for the decorations---space
+                           % that disappears at page breaks.
+                           beforeafter skip=28pt}
+}
 
@@
 \end{DndTable}
+
+The |ornamentedtabular| allows tables similar to those used for spellcasters
+(see over page).
+
+\begin{figure*}[h]
+\begin{ornamentedtabular}{cclccccccccccc}[title={The Full Caster}]
+  & & & & & \multicolumn{9}{c}{\thead{--- Spell Slots per Spell Level ---}} \\
+  \textbf{Level} & \textbf{\makecell{Proficiency\\Bonus}} & \textbf{Features} & \textbf{\makecell{Cantrips\\Known}} & \textbf{\makecell{Spells\\Known}} & \textbf{1st} & \textbf{2nd} & \textbf{3rd} & \textbf{4th} & \textbf{5th} & \textbf{6th} & \textbf{7th} & \textbf{8th} & \textbf{9th} \\
+  1st  & +2 & Feature & 3 & 4  & 2 & — & — & — & — & — & — & — & — \\
+  2nd  & +2 & Feature & 3 & 4  & 3 & — & — & — & — & — & — & — & — \\
+  3rd  & +2 & Feature & 4 & 4  & 4 & 2 & — & — & — & — & — & — & — \\
+  4th  & +2 & Feature & 4 & 5  & 4 & 3 & — & — & — & — & — & — & — \\
+  5th  & +3 & Feature & 4 & 6  & 4 & 3 & 2 & — & — & — & — & — & — \\
+  6th  & +3 & Feature & 4 & 7  & 4 & 3 & 3 & — & — & — & — & — & — \\
+  7th  & +3 & Feature & 4 & 8  & 4 & 3 & 3 & 1 & — & — & — & — & — \\
+  8th  & +3 & Feature & 4 & 9  & 4 & 3 & 3 & 2 & — & — & — & — & — \\
+  9th  & +4 & Feature & 4 & 10 & 4 & 3 & 3 & 3 & 1 & — & — & — & — \\
+  10th & +4 & Feature & 5 & 11 & 4 & 3 & 3 & 3 & 2 & — & — & — & — \\
+  11th & +4 & Feature & 5 & 12 & 4 & 3 & 3 & 3 & 2 & 1 & — & — & — \\
+  12th & +4 & Feature & 5 & 12 & 4 & 3 & 3 & 3 & 2 & 1 & — & — & — \\
+  13th & +4 & Feature & 5 & 13 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & — & — \\
+  14th & +5 & Feature & 5 & 13 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & — & — \\
+  15th & +5 & Feature & 5 & 14 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & — \\
+  16th & +5 & Feature & 5 & 14 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & — \\
+  17th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & 1 \\
+  18th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 1 & 1 & 1 & 1 \\
+  19th & +6 & Feature & 4 & 15 & 4 & 3 & 3 & 3 & 3 & 2 & 1 & 1 & 1 \\
+  20th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 2 & 2 & 1 & 1 \\
+\end{ornamentedtabular}
+\end{figure*}
 

### 2020-08-03 table-examples.tex
Moved table stuff to a separate tex file so it doesn't pollute the regular article

\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode]{dndbook}

% Use babel or polyglossia to automatically redefine macros for terms
% Armor Class, Level, etc...
% Default output is in English; captions are located in lib/dndstrings.sty.
% If no captions exist for a language, English will be used.
%1. To load a language with babel:
%	\usepackage[<lang>]{babel}
%2. To load a language with polyglossia:
%	\usepackage{polyglossia}
%	\setdefaultlanguage{<lang>}
\usepackage[english]{babel}
%\usepackage[italian]{babel}
% For further options (multilanguage documents, hypenations, language environments...)
% please refer to babel/polyglossia's documentation.

\usepackage[utf8]{inputenc}
\usepackage[singlelinecheck=false]{caption}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{shortvrb}
\usepackage{stfloats}
\usepackage{xtab}
\usetikzlibrary{intersections}

\captionsetup[table]{labelformat=empty,font={sf,sc,bf,},skip=0pt}

% Uncomment to allow the default background paper image to be overridden.
%\SetPaperImage{img/paper}

\MakeShortVerb{|}

\lstset{%
  basicstyle=\ttfamily,
  language=[LaTeX]{TeX},
  breaklines=true,
}

\title{The Dark \LaTeX{} \\
\large An Example of the dndbook Class}
\author{The rpgTeX Team}
\date{2020/04/21}

%%%%%%%%%%%%% START "ornamented table" CODE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Code from Loop Space: <https://tex.stackexchange.com/a/26386/73317>
\makeatletter
\tikzset{
  use path for main/.code={%
    \tikz@addmode{%
      \expandafter\pgfsyssoftpath@setcurrentpath\csname tikz@intersect@path@name@#1\endcsname
    }%
  },
  use path for actions/.code={%
    \expandafter\def\expandafter\tikz@preactions\expandafter{\tikz@preactions\expandafter\let\expandafter\tikz@actions@path\csname tikz@intersect@path@name@#1\endcsname}%
  },
  use path/.style={%
    use path for main=#1,
    use path for actions=#1,
  }
}
\makeatother
% End of the code from Loop Space

% Ornamented box content from: https://tex.stackexchange.com/a/501736/2575
% TODO: Work out how to get the rest of the content from here into the dndtable.sty
%       file, which causes errors like:
%         ! Package pgfkeys Error: I do not know the key '/tcb/skinfirst'
\tikzset{ornamented frame inner/.style={color=ornamentedFrameInner,
                                        line width=2pt},
         ornamented frame outer/.style={color=ornamentedFrameOuter,
                                        line width=3pt}}

\tcbsubskin{ornamented}{empty}{
  skin first=ornamented, skin middle=ornamented, skin last=ornamented,
  title engine=standard,
  frame code={
    % Account for the line widths in order not to draw beyond the bounding
    % box---except for a few very small details for which this is intentional.
    \coordinate (north west) at ([shift={(-1.5pt,9.5pt)}]frame.north west);
    \coordinate (north east) at ([shift={(1.5pt,9.5pt)}]frame.north east);
    \coordinate (south east) at ([shift={(1.5pt,-9.5pt)}]frame.south east);
    \coordinate (south west) at ([shift={(-1.5pt,-9.5pt)}]frame.south west);
    %
    \foreach \xoffset/\point in {34pt/north west, -34pt/north east,
                                  34pt/south west, -34pt/south east} {
      \fill[color=ornamentedFrameOuter]
        ([xshift=\xoffset]\point) circle[radius=2.5pt];
    }
    %
    \path[name path=ornament 1]  ([yshift=-4pt]north west)
      [rounded corners=0.5pt] -- ++(23pt,0)
      [rounded corners=2pt]   -- ++(3pt,-4pt)
                              -- ([shift={(-26pt,-8pt)}]north east)
      [rounded corners=0.5pt] -- ++(3pt,4pt)
      [rounded corners=4pt]   -- ([yshift=-4pt]north east)
                              -- ([yshift=4pt]south east)
      [rounded corners=0.5pt] -- ++(-23pt,0)
      [rounded corners=2pt]   -- ++(-3pt,4pt)
                              -- ([shift={(26pt,8pt)}]south west)
      [rounded corners=0.5pt] -- ++(-3pt,-4pt)
      [rounded corners=4pt]   -- ([yshift=4pt]south west)
                              -- cycle;
    %
    \path[rounded corners=0.5pt, name path=ornament 2]
                                 ([yshift=-20pt]north west)
                              -- ++(-4pt,3pt)
                              -- ++(0,4pt)
               to[out=0, in=-90] ([shift={(8pt,0pt)}]north west)
                              -- ([shift={(34pt,0pt)}]north west)
                              -- ([shift={(-8pt,0pt)}]north east)
             to[out=-90, in=180] ([shift={(4pt,-13pt)}]north east)
                              -- ++(0,-4pt)
                              -- ++(-4pt,-3pt)
                              -- ([yshift=20pt]south east)
                              -- ++(4pt,-3pt)
                              -- ++(0,-4pt)
              to[out=180, in=90] ([shift={(-8pt,0pt)}]south east)
                              -- ([shift={(8pt,0pt)}]south west)
                to[out=90, in=0] ([shift={(-4pt,13pt)}]south west)
                              -- ++(0,4pt)
                              -- ++(4pt,3pt)
                              -- cycle;
    %
    \draw[ornamented frame outer, use path=ornament 1,fill=white];
    \draw[ornamented frame outer, use path=ornament 2];
    \draw[ornamented frame inner, use path=ornament 1];
    \draw[ornamented frame inner, use path=ornament 2];
    %
    \foreach \xoffset/\point in {34pt/north west, -34pt/north east,
                                 34pt/south west, -34pt/south east} {
      \fill[color=ornamentedFrameInner]
        ([xshift=\xoffset]\point) circle[radius=2pt];
    }
  }
}

% These parameters---especially those related to geometry---are better located
% here in a style than in the subskin definition (see the Subskins section of
% the tcolorbox manual).
\tcbset{ornamented/.style={skin=ornamented, coltitle=black, toptitle=5pt,
                           % Reserve vertical space for the decorations---space
                           % that disappears at page breaks.
                           beforeafter skip=28pt}
}
%%%%%%%%%%%%% END "ornamented table" CODE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%% START "dndlongtable" CODE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Normally, @ is not a valid character in macro names. Make the @ symbol a
% normal letter in order to call an internal command from the dnd package.
% See <https://tex.stackexchange.com/a/8353> for more information.
\makeatletter
\NewDocumentEnvironment{dndlongtable}{O{>{\centering}p{0.2\linewidth} p{0.7\linewidth}} O{tablecolor}}{%
  % End horizontal mode. Pad the top of the table with some vertical space.
  \par\vspace*{8pt}
  % Disable indentation on the next line.
  \noindent
  % Set the sans-serif table body font.
  \DndFontTableBody
  % Set alternating row colours.
  \rowcolors{1}{}{#2}
  % Create an `xtabular*` table as wide as the current line (column) and pass
  % the column spec to it (#1).
  \begin{xtabular*}{\linewidth}{#1}
}{%
  \end{xtabular*}
  % Pad the bottom of the table with some vertical space.
  \vspace{8pt plus 1pt}
  % Disable indentation on the next line.
  \noindent
}
% Disable the @ character in macro names again.
\makeatother
%%%%%%%%%%%%% END "dndlongtable" CODE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\frontmatter

\maketitle

\tableofcontents

\mainmatter%

\part{Layout}

\chapter{Sections}

\DndDropCapLine{T}{his package is designed to aid you in} writing beautifully typeset documents for the fifth edition of the world's greatest roleplaying game. It starts by adjusting the section formatting from the defaults in \LaTeX{} to something a bit more familiar to the reader. The chapter formatting is displayed above.

\section{Tables}
The |DndTable| colors the even rows and is set to the width of a line by default.

\begin{DndTable}[header=Nice Table]{XX}
    \textbf{Table head}  & \textbf{Table head} \\
    Some value  & Some value \\
    Some value  & Some value \\
    Some value  & Some value
\end{DndTable}

\section{Table Options}
Examples of different table types that can be added when needed.

\subparagraph{Note} These examples are currently in a separate file
(|table-examples.tex|) because some of the code only works
when embedded in the |.tex| file. They'll be moved if/when that code
can be cleaned up.

\subsection{Alternate Table Background}

The |DndAltTable| allows tables that have a blank "header" line followed
by alternating theme color and white background, as per some of the sourcebooks.

\begin{DndAltTable}{cX}
    \textbf{Table head} & \textbf{Table head} \\
    Some value  & Some value \\
    Some value  & Some value \\
    Some value  & Some value \\
    Some value  & Some value \\
\end{DndAltTable}

\subsection{Long Table that Spans Pages}

The |dndlongtable| allows table that can span multiple pages. The current
version is configured to do a two-column table.

\begin{dndlongtable}
    \textbf{Roll (d100)} & \textbf{Result} \\
    1-2 & You win a magic item or an expensive piece of classic artwork. \\
    3-4 & You win a magic item or an expensive piece of classic artwork. \\
    5-6 & You win a magic item or an expensive piece of classic artwork. \\
    7-8 & You win a magic item or an expensive piece of classic artwork. \\
    9-10 & You win a magic item or an expensive piece of classic artwork. \\
    11-12 & You win a magic item or an expensive piece of classic artwork. \\
    13-14 & You win a magic item or an expensive piece of classic artwork. \\
    15-16 & You win a magic item or an expensive piece of classic artwork. \\
    17-18 & You win a magic item or an expensive piece of classic artwork. \\
    19-20 & You win a magic item or an expensive piece of classic artwork. \\
    20-22 & You win a magic item or an expensive piece of classic artwork. \\
    23-24 & You win a magic item or an expensive piece of classic artwork. \\
    25-26 & You win a magic item or an expensive piece of classic artwork. \\
    27-28 & You win a magic item or an expensive piece of classic artwork. \\
    29-30 & You win a magic item or an expensive piece of classic artwork. \\
    31-32 & You win a magic item or an expensive piece of classic artwork. \\
    33-34 & You win a magic item or an expensive piece of classic artwork. \\
    35-36 & You win a magic item or an expensive piece of classic artwork. \\
    37-38 & You win a magic item or an expensive piece of classic artwork. \\
    39-40 & You win a magic item or an expensive piece of classic artwork. \\
    41-42 & You win a magic item or an expensive piece of classic artwork. \\
    43-44 & You win a magic item or an expensive piece of classic artwork. \\
    45-46 & You win a magic item or an expensive piece of classic artwork. \\
    47-48 & You win a magic item or an expensive piece of classic artwork. \\
    49-50 & You win a magic item or an expensive piece of classic artwork. \\
    51-52 & You win a magic item or an expensive piece of classic artwork. \\
    53-54 & You win a magic item or an expensive piece of classic artwork. \\
    55-56 & You win a magic item or an expensive piece of classic artwork. \\
    57-58 & You win a magic item or an expensive piece of classic artwork. \\
    59-60 & You win a magic item or an expensive piece of classic artwork. \\
    61-62 & You win a magic item or an expensive piece of classic artwork. \\
    63-64 & You win a magic item or an expensive piece of classic artwork. \\
    65-66 & You win a magic item or an expensive piece of classic artwork. \\
    67-68 & You win a magic item or an expensive piece of classic artwork. \\
    69-70 & You win a magic item or an expensive piece of classic artwork. \\
    71-72 & You win a magic item or an expensive piece of classic artwork. \\
    73-74 & You win a magic item or an expensive piece of classic artwork. \\
    75-76 & You win a magic item or an expensive piece of classic artwork. \\
    77-78 & You win a magic item or an expensive piece of classic artwork. \\
    79-80 & You win a magic item or an expensive piece of classic artwork. \\
    81 & You win a magic item or an expensive piece of classic artwork. \\
    82 & You win a magic item or an expensive piece of classic artwork. \\
    83 & You win a magic item or an expensive piece of classic artwork. \\
    84 & You win a magic item or an expensive piece of classic artwork. \\
    85 & You win a magic item or an expensive piece of classic artwork. \\
    86 & You win a magic item or an expensive piece of classic artwork. \\
    87 & You win a magic item or an expensive piece of classic artwork. \\
    88 & You win a magic item or an expensive piece of classic artwork. \\
    89 & You win a magic item or an expensive piece of classic artwork. \\
    90 & You win a magic item or an expensive piece of classic artwork. \\
    91 & You win a magic item or an expensive piece of classic artwork. \\
    92 & You win a magic item or an expensive piece of classic artwork. \\
    93 & You win a magic item or an expensive piece of classic artwork. \\
    94 & You win a magic item or an expensive piece of classic artwork. \\
    95 & You win a magic item or an expensive piece of classic artwork. \\
    96 & You win a magic item or an expensive piece of classic artwork. \\
    97 & You win a magic item or an expensive piece of classic artwork. \\
    98 & You win a magic item or an expensive piece of classic artwork. \\
    99 & You win a magic item or an expensive piece of classic artwork. \\
    100 & You win a magic item or an expensive piece of classic artwork. \\
\end{dndlongtable}

\subsection{Ornamented Tables}
The |ornamentedtabular| allows tables similar to those used for spellcasters
(see over page).

\begin{figure*}[h!]
\begin{ornamentedtabular}{ccp{3.0cm}ccccccccccc}[title={The Full Caster}]
  & & & & & \multicolumn{9}{c}{\thead{--- Spell Slots per Spell Level ---}} \\
  \textbf{Level} & \textbf{\makecell{Proficiency\\Bonus}} & \textbf{Features} & \textbf{\makecell{Cantrips\\Known}} & \textbf{\makecell{Spells\\Known}} & \textbf{1st} & \textbf{2nd} & \textbf{3rd} & \textbf{4th} & \textbf{5th} & \textbf{6th} & \textbf{7th} & \textbf{8th} & \textbf{9th} \\
  1st  & +2 & Feature & 3 & 4  & 2 & — & — & — & — & — & — & — & — \\
  2nd  & +2 & Feature & 3 & 4  & 3 & — & — & — & — & — & — & — & — \\
  3rd  & +2 & Feature & 4 & 4  & 4 & 2 & — & — & — & — & — & — & — \\
  4th  & +2 & Feature & 4 & 5  & 4 & 3 & — & — & — & — & — & — & — \\
  5th  & +3 & Feature & 4 & 6  & 4 & 3 & 2 & — & — & — & — & — & — \\
  6th  & +3 & Feature & 4 & 7  & 4 & 3 & 3 & — & — & — & — & — & — \\
  7th  & +3 & Feature & 4 & 8  & 4 & 3 & 3 & 1 & — & — & — & — & — \\
  8th  & +3 & Feature & 4 & 9  & 4 & 3 & 3 & 2 & — & — & — & — & — \\
  9th  & +4 & Feature & 4 & 10 & 4 & 3 & 3 & 3 & 1 & — & — & — & — \\
  10th & +4 & Feature & 5 & 11 & 4 & 3 & 3 & 3 & 2 & — & — & — & — \\
  11th & +4 & Feature & 5 & 12 & 4 & 3 & 3 & 3 & 2 & 1 & — & — & — \\
  12th & +4 & Feature & 5 & 12 & 4 & 3 & 3 & 3 & 2 & 1 & — & — & — \\
  13th & +4 & Feature & 5 & 13 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & — & — \\
  14th & +5 & Feature & 5 & 13 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & — & — \\
  15th & +5 & Feature & 5 & 14 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & — \\
  16th & +5 & Feature & 5 & 14 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & — \\
  17th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & 1 \\
  18th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 1 & 1 & 1 & 1 \\
  19th & +6 & Feature & 4 & 15 & 4 & 3 & 3 & 3 & 3 & 2 & 1 & 1 & 1 \\
  20th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 2 & 2 & 1 & 1 \\
\end{ornamentedtabular}
\end{figure*}

\part{Customization}

\chapter{Colors}

\begin{table*}[b]
  \caption{\DndFontTableTitle{}Colors Supported by this Package}\label{tab:colors}

  \begin{tabularx}{\linewidth}{lX}
    \textbf{Color}                  & \textbf{Description} \\
    \rowcolor{PhbLightGreen}
    |PhbLightGreen|                 & Light green used in PHB Part 1 (Default) \\
    \rowcolor{PhbLightCyan}
    |PhbLightCyan|                  & Light cyan used in PHB Part 2 \\
    \rowcolor{PhbMauve}
    |PhbMauve|                      & Pale purple used in PHB Part 3 \\
    \rowcolor{PhbTan}
    |PhbTan|                        & Light brown used in PHB appendix \\
    \rowcolor{DmgLavender}
    |DmgLavender|                   & Pale purple used in DMG Part 1 \\
    \rowcolor{DmgCoral}
    |DmgCoral|                      & Orange-pink used in DMG Part 2 \\
    \rowcolor{DmgSlateGray}
    |DmgSlateGray| (|DmgSlateGrey|) & Blue-gray used in PHB Part 3 \\
    \rowcolor{DmgLilac}
    |DmgLilac|                      & Purple-gray used in DMG appendix \\
    \rowcolor{BrGreen}
    |BrGreen|                       & Gray-green used for tables in Basic Rules\\
  \end{tabularx}
\end{table*}

This package provides several global color variables to style |DndComment|, |DndReadAloud|, |DndSidebar|, and |DndTable| environments.

\begin{DndTable}[header=Box Colors]{lX}
  \textbf{Color}   & \textbf{Description} \\
  |commentcolor|   & |DndComment| background \\
  |readaloudcolor| & |DndReadAloud| background \\
  |sidebarcolor|   & |DndSidebar| background \\
  |tablecolor|     & background of even |DndTable| rows \\
\end{DndTable}

They also accept an optional color argument to set the color for a single instance. See Table~\ref{tab:colors} for a list of core book accent colors.

\begin{lstlisting}
\begin{DndTable}[color=PhbLightCyan]{cX}
  \textbf{d8} & \textbf{Item} \\
  1 & Small wooden button \\
  2 & Red feather \\
  3 & Human tooth \\
  4 & Vial of green liquid \\
  6 & Tasty biscuit \\
  7 & Broken axe handle \\
  8 & Tarnished silver locket \\
\end{DndTable}
\end{lstlisting}

\begin{DndTable}[color=PhbLightCyan]{cX}
  \textbf{d8} & \textbf{Item} \\
  1 & Small wooden button \\
  2 & Red feather \\
  3 & Human tooth \\
  4 & Vial of green liquid \\
  6 & Tasty biscuit \\
  7 & Broken axe handle \\
  8 & Tarnished silver locket \\
\end{DndTable}

\section{Themed Colors}
Use |\DndSetThemeColor[<color>]| to set |commentcolor|, |readaloudcolor|, |sidebarcolor|, and |tablecolor| to a specific color. Calling |\DndSetThemeColor| without an argument sets those colors to the current |themecolor|. In the following example the group limits the change to just a few boxes; after the group finishes, the colors are reverted to what they were before the group started.

\begin{lstlisting}
\begingroup
\DndSetThemeColor[PhbMauve]

\begin{DndComment}{This Comment Is in Mauve}
  This comment is in the the new color.
\end{DndComment}

\begin{DndSidebar}{This Sidebar Is Also Mauve}
  The sidebar is also using the new theme color.
\end{DndSidebar}
\endgroup
\end{lstlisting}

\begingroup
\DndSetThemeColor[PhbMauve]

\begin{DndComment}{This Comment Is in Mauve}
  This comment is in the the new color.
\end{DndComment}

\begin{DndSidebar}{This Sidebar Is Also Mauve}
  The sidebar is also using the new theme color.
\end{DndSidebar}
\endgroup

\end{document}

### 2020-09-13 article.tex
Added example usage of new theme color control option
Added the "letteredarea" example and tweaked the alternate map layout section

@@
 \SetPaperImage{img/paper-article}
+
+% The settings below are an example of how to modify all of the theme colors.
+% Note that the paper (\SetPaperImage) and footerscroll.pdf will probably need
+% to be modified for any % major color scheme change. The values below are
+% thematic for a sourcebook like GoS.
+\definecolor {mytheme}      {HTML} {DCF1E5} %
+\definecolor {mysidebar}    {HTML} {E9F5F5} %
+\definecolor {myreadaloud}  {HTML} {DCF1E5} %
+\definecolor {myreadaloudborder}  {HTML} {8AA7A2} %
+\definecolor {mypagenum}  {HTML} {B5D4CF} %
+%\DndSetComplexThemeColor[mytheme][mysidebar][myreadaloud][myreadaloudborder][titlered][titlegold][mypagenum]
 
@@
 \section{Alternate Map Region Styles}
-Published modules sometimes use plain numbers for locations, sometimes they
-prefix a character to the front of the numbers. The following options can be
-used to display in these forms:
+Published modules sometimes use plain numbers for locations, sometimes plain
+letters, and sometimes they prefix a character to the front of the numbers.
+The following options can be used to display in these forms:
 
@@
 
+These commands yield the following results:
 \numberedsubarea{Entry}
@@
 
-\prefixedarea{Ace Dungeon}{A}
-Areas in the Ace Dungeon are prefixed with `\prefixedareaprefix'.
+\letteredarea{Lettered Dungeon}
+Areas in the Lettered Dungeon are labelled with sequential characters
+(A, B, C, etc). This is done using the following commands:
+
+\begin{verbatim}
+\letteredarea{Lettered Dungeon}
+\letteredsubarea{Entry}
+\letteredsubarea{Trap}
+\letteredsubarea{Fight}
+\letteredsubarea{Exit}
+\end{verbatim}
+
+These commands yield the following results:
+\letteredsubarea{Entry}
+\letteredsubarea{Trap}
+\letteredsubarea{Fight}
+\letteredsubarea{Exit}
+
+\prefixedarea{Prefixed Dungeon}{Z}
+Areas in the Prefixed Dungeon have a custom prefix character,
+in this case: `\prefixedareaprefix'.
 This is done using the following commands:
@@
 \begin{verbatim}
-\prefixedarea{Ace Dungeon}{A}
+\prefixedarea{Prefixed Dungeon}{Z}
 \prefixedsubarea{Entry}
+\prefixedsubarea{Trap}
+\prefixedsubarea{Fight}
 \prefixedsubarea{Exit}
@@
 
+These commands yield the following results:
 \prefixedsubarea{Entry}
-\prefixedsubarea{Exit}
-
-\prefixedarea{The Fantastic Zoo}{Z}
-Areas in the Fantastic Zoo are prefixed with `\prefixedareaprefix'.
-
-\prefixedsubarea{Entry}
+\prefixedsubarea{Trap}
+\prefixedsubarea{Fight}
 \prefixedsubarea{Exit}

### 2020-09-13 example.tex
Added a section for "alternate map regions" to demonstrate the additional options

@@
 \usepackage{stfloats}
+\usepackage{lmodern} % Scalable font
+\usepackage{lettrine} % For the drop cap
 
@@
 \author{The rpgTeX Team}
-\date{2019/07/18}
+\date{2020/04/21}
 
@@
 
+\section{Alternate Map Region Styles}
+Published modules sometimes use plain numbers for locations, sometimes plain
+letters, and sometimes they prefix a character to the front of the numbers.
+The following options can be used to display in these forms:
+
+\numberedarea{Numbered Dungeon}
+Areas in the Numbered Dungeon have sequential numbers. This is done using
+the following commands:
+
+\begin{verbatim}
+\numberedarea{Numbered Dungeon}
+\numberedsubarea{Entry}
+\numberedsubarea{Trap}
+\numberedsubarea{Fight}
+\numberedsubarea{Exit}
+\end{verbatim}
+
+These commands yield the following results:
+\numberedsubarea{Entry}
+\numberedsubarea{Trap}
+\numberedsubarea{Fight}
+\numberedsubarea{Exit}
+
+\letteredarea{Lettered Dungeon}
+Areas in the Lettered Dungeon are labelled with sequential characters
+(A, B, C, etc). This is done using the following commands:
+
+\begin{verbatim}
+\letteredarea{Lettered Dungeon}
+\letteredsubarea{Entry}
+\letteredsubarea{Trap}
+\letteredsubarea{Fight}
+\letteredsubarea{Exit}
+\end{verbatim}
+
+These commands yield the following results:
+\letteredsubarea{Entry}
+\letteredsubarea{Trap}
+\letteredsubarea{Fight}
+\letteredsubarea{Exit}
+
+\prefixedarea{Prefixed Dungeon}{Z}
+Areas in the Prefixed Dungeon have a custom prefix character,
+in this case: `\prefixedareaprefix'.
+This is done using the following commands:
+
+\begin{verbatim}
+\prefixedarea{Prefixed Dungeon}{Z}
+\prefixedsubarea{Entry}
+\prefixedsubarea{Trap}
+\prefixedsubarea{Fight}
+\prefixedsubarea{Exit}
+\end{verbatim}
+
+These commands yield the following results:
+\prefixedsubarea{Entry}
+\prefixedsubarea{Trap}
+\prefixedsubarea{Fight}
+\prefixedsubarea{Exit}
+
 \chapter{Text Boxes}
@@
 \begin{DndTable}[header=Nice Table]{XX}
-    \textbf{Table head}  & \textbf{Table head} \\
+    Table head  & Table head \\
     Some value  & Some value \\
@@
 \begin{table*}[b]
-  \caption{\DndFontTableTitle{}Colors Supported by this Package\label{tab:colors}}
+  \caption{\DndFontTableTitle{}Colors Supported by this Package}\label{tab:colors}
 
@@
 \begin{DndTable}[header=Box Colors]{lX}
-  \textbf{Color}   & \textbf{Description} \\
+  Color            &  Description \\
   |commentcolor|   & |DndComment| background \\
@@
 \begin{DndTable}[color=PhbLightCyan]{cX}
-  \textbf{d8} & \textbf{Item} \\
+  d8 & Item \\
   1  & Small wooden button \\
@@
   4  & Vial of green liquid \\
+  5  & Loaded dice \\
   6  & Tasty biscuit \\

### 2020-09-13 example.tex
Added a section for "alternate map regions" to demonstrate the additional options

--- 2020-04-18 example.tex
@@
 A five-foot hole reveals the dirt floor illuminated by a hole in the roof.
+
+\section{Alternate Map Region Styles}
+Published modules sometimes use plain numbers for locations, sometimes plain
+letters, and sometimes they prefix a character to the front of the numbers.
+The following options can be used to display in these forms:
+
+\numberedarea{Numbered Dungeon}
+Areas in the Numbered Dungeon have sequential numbers. This is done using
+the following commands:
+
+\begin{verbatim}
+\numberedarea{Numbered Dungeon}
+\numberedsubarea{Entry}
+\numberedsubarea{Trap}
+\numberedsubarea{Fight}
+\numberedsubarea{Exit}
+\end{verbatim}
+
+These commands yield the following results:
+\numberedsubarea{Entry}
+\numberedsubarea{Trap}
+\numberedsubarea{Fight}
+\numberedsubarea{Exit}
+
+\letteredarea{Lettered Dungeon}
+Areas in the Lettered Dungeon are labelled with sequential characters
+(A, B, C, etc). This is done using the following commands:
+
+\begin{verbatim}
+\letteredarea{Lettered Dungeon}
+\letteredsubarea{Entry}
+\letteredsubarea{Trap}
+\letteredsubarea{Fight}
+\letteredsubarea{Exit}
+\end{verbatim}
+
+These commands yield the following results:
+\letteredsubarea{Entry}
+\letteredsubarea{Trap}
+\letteredsubarea{Fight}
+\letteredsubarea{Exit}
+
+\prefixedarea{Prefixed Dungeon}{Z}
+Areas in the Prefixed Dungeon have a custom prefix character,
+in this case: `\prefixedareaprefix'.
+This is done using the following commands:
+
+\begin{verbatim}
+\prefixedarea{Prefixed Dungeon}{Z}
+\prefixedsubarea{Entry}
+\prefixedsubarea{Trap}
+\prefixedsubarea{Fight}
+\prefixedsubarea{Exit}
+\end{verbatim}
+
+These commands yield the following results:
+\prefixedsubarea{Entry}
+\prefixedsubarea{Trap}
+\prefixedsubarea{Fight}
+\prefixedsubarea{Exit}
 

### 2020-10-08 table-examples.tex
Added an example of a table with footnotes that are "attached" to the table (not placed at the bottom of the page like a normal footnote)
Fixed issue with "ornamented tabular" breaking when moved into lib/dndtable.sty

@@
 \date{2020/04/21}
-
-%%%%%%%%%%%%% START "ornamented table" CODE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Code from Loop Space: <https://tex.stackexchange.com/a/26386/73317>
-\makeatletter
-\tikzset{
-  use path for main/.code={%
-    \tikz@addmode{%
-      \expandafter\pgfsyssoftpath@setcurrentpath\csname tikz@intersect@path@name@#1\endcsname
-    }%
-  },
-  use path for actions/.code={%
-    \expandafter\def\expandafter\tikz@preactions\expandafter{\tikz@preactions\expandafter\let\expandafter\tikz@actions@path\csname tikz@intersect@path@name@#1\endcsname}%
-  },
-  use path/.style={%
-    use path for main=#1,
-    use path for actions=#1,
-  }
-}
-\makeatother
-% End of the code from Loop Space
-
-% Ornamented box content from: https://tex.stackexchange.com/a/501736/2575
-% TODO: Work out how to get the rest of the content from here into the dndtable.sty
-%       file, which causes errors like:
-%         ! Package pgfkeys Error: I do not know the key '/tcb/skinfirst'
-\tikzset{ornamented frame inner/.style={color=ornamentedFrameInner,
-                                        line width=2pt},
-         ornamented frame outer/.style={color=ornamentedFrameOuter,
-                                        line width=3pt}}
-
-\tcbsubskin{ornamented}{empty}{
-  skin first=ornamented, skin middle=ornamented, skin last=ornamented,
-  title engine=standard,
-  frame code={
-    % Account for the line widths in order not to draw beyond the bounding
-    % box---except for a few very small details for which this is intentional.
-    \coordinate (north west) at ([shift={(-1.5pt,9.5pt)}]frame.north west);
-    \coordinate (north east) at ([shift={(1.5pt,9.5pt)}]frame.north east);
-    \coordinate (south east) at ([shift={(1.5pt,-9.5pt)}]frame.south east);
-    \coordinate (south west) at ([shift={(-1.5pt,-9.5pt)}]frame.south west);
-    %
-    \foreach \xoffset/\point in {34pt/north west, -34pt/north east,
-                                  34pt/south west, -34pt/south east} {
-      \fill[color=ornamentedFrameOuter]
-        ([xshift=\xoffset]\point) circle[radius=2.5pt];
-    }
-    %
-    \path[name path=ornament 1]  ([yshift=-4pt]north west)
-      [rounded corners=0.5pt] -- ++(23pt,0)
-      [rounded corners=2pt]   -- ++(3pt,-4pt)
-                              -- ([shift={(-26pt,-8pt)}]north east)
-      [rounded corners=0.5pt] -- ++(3pt,4pt)
-      [rounded corners=4pt]   -- ([yshift=-4pt]north east)
-                              -- ([yshift=4pt]south east)
-      [rounded corners=0.5pt] -- ++(-23pt,0)
-      [rounded corners=2pt]   -- ++(-3pt,4pt)
-                              -- ([shift={(26pt,8pt)}]south west)
-      [rounded corners=0.5pt] -- ++(-3pt,-4pt)
-      [rounded corners=4pt]   -- ([yshift=4pt]south west)
-                              -- cycle;
-    %
-    \path[rounded corners=0.5pt, name path=ornament 2]
-                                 ([yshift=-20pt]north west)
-                              -- ++(-4pt,3pt)
-                              -- ++(0,4pt)
-               to[out=0, in=-90] ([shift={(8pt,0pt)}]north west)
-                              -- ([shift={(34pt,0pt)}]north west)
-                              -- ([shift={(-8pt,0pt)}]north east)
-             to[out=-90, in=180] ([shift={(4pt,-13pt)}]north east)
-                              -- ++(0,-4pt)
-                              -- ++(-4pt,-3pt)
-                              -- ([yshift=20pt]south east)
-                              -- ++(4pt,-3pt)
-                              -- ++(0,-4pt)
-              to[out=180, in=90] ([shift={(-8pt,0pt)}]south east)
-                              -- ([shift={(8pt,0pt)}]south west)
-                to[out=90, in=0] ([shift={(-4pt,13pt)}]south west)
-                              -- ++(0,4pt)
-                              -- ++(4pt,3pt)
-                              -- cycle;
-    %
-    \draw[ornamented frame outer, use path=ornament 1,fill=white];
-    \draw[ornamented frame outer, use path=ornament 2];
-    \draw[ornamented frame inner, use path=ornament 1];
-    \draw[ornamented frame inner, use path=ornament 2];
-    %
-    \foreach \xoffset/\point in {34pt/north west, -34pt/north east,
-                                 34pt/south west, -34pt/south east} {
-      \fill[color=ornamentedFrameInner]
-        ([xshift=\xoffset]\point) circle[radius=2pt];
-    }
-  }
-}
-
-% These parameters---especially those related to geometry---are better located
-% here in a style than in the subskin definition (see the Subskins section of
-% the tcolorbox manual).
-\tcbset{ornamented/.style={skin=ornamented, coltitle=black, toptitle=5pt,
-                           % Reserve vertical space for the decorations---space
-                           % that disappears at page breaks.
-                           beforeafter skip=28pt}
-}
-%%%%%%%%%%%%% END "ornamented table" CODE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\subsection{Tables with Footnotes}
+
+\begin{minipage}{8cm}
+  \begin{DndTable}[header=Footnoted Table]{lX}
+    \textbf{Table head\footnote{\enspace Something to note}} & \textbf{Table head} \\
+    Some value  & Some value\footnote{\enspace Another thing to note} \\
+    Some value  & Some value \\
+    Some value  & Some value \\
+    Some value\footnote{\enspace The most important note}  & Some value \\
+  \end{DndTable}
+\end{minipage}
+
 \subsection{Ornamented Tables}

### 2020-10-09 table-examples.tex
Fixed typos in the example "full caster" table

@@
   2nd  & +2 & Feature & 3 & 4  & 3 & — & — & — & — & — & — & — & — \\
-  3rd  & +2 & Feature & 4 & 4  & 4 & 2 & — & — & — & — & — & — & — \\
+  3rd  & +2 & Feature & 3 & 4  & 4 & 2 & — & — & — & — & — & — & — \\
   4th  & +2 & Feature & 4 & 5  & 4 & 3 & — & — & — & — & — & — & — \\
@@
   12th & +4 & Feature & 5 & 12 & 4 & 3 & 3 & 3 & 2 & 1 & — & — & — \\
-  13th & +4 & Feature & 5 & 13 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & — & — \\
+  13th & +5 & Feature & 5 & 13 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & — & — \\
   14th & +5 & Feature & 5 & 13 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & — & — \\
@@
   18th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 1 & 1 & 1 & 1 \\
-  19th & +6 & Feature & 4 & 15 & 4 & 3 & 3 & 3 & 3 & 2 & 1 & 1 & 1 \\
+  19th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 2 & 1 & 1 & 1 \\
   20th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 2 & 2 & 1 & 1 \\

### 2020-12-22 example.tex
Moved the "alternate" table examples over to the core example.tex file

--- 2020-09-13 example.tex
@@
 \usepackage{lettrine} % For the drop cap
+\usetikzlibrary{intersections} % Required for ornamentedtabular
 
@@
 \section{Tables}
+
+\subsection{Regular Table}
 The |DndTable| colors the even rows and is set to the width of a line by default.
@@
 \end{DndTable}
+
+\subsection{Alternate Table Background}
+
+The |DndAltTable| allows tables that have a blank "header" line followed
+by alternating theme color and white background, as per some of the sourcebooks.
+
+\begin{DndAltTable}{cX}
+    \textbf{Table head} & \textbf{Table head} \\
+    Some value  & Some value \\
+    Some value  & Some value \\
+    Some value  & Some value \\
+    Some value  & Some value \\
+\end{DndAltTable}
+
+\subsection{Long Table that Spans Pages}
+
+The |dndlongtable| allows table that can span multiple pages. The current
+version is configured to do a two-column table.
+
+\begin{dndlongtable}
+    \textbf{Roll (d100)} & \textbf{Result} \\
+    1-2 & You win a magic item or an expensive piece of classic artwork. \\
+    3-4 & You win a magic item or an expensive piece of classic artwork. \\
+    5-6 & You win a magic item or an expensive piece of classic artwork. \\
+    7-8 & You win a magic item or an expensive piece of classic artwork. \\
+    9-10 & You win a magic item or an expensive piece of classic artwork. \\
+    11-12 & You win a magic item or an expensive piece of classic artwork. \\
+    13-14 & You win a magic item or an expensive piece of classic artwork. \\
+    15-16 & You win a magic item or an expensive piece of classic artwork. \\
+    17-18 & You win a magic item or an expensive piece of classic artwork. \\
+    19-20 & You win a magic item or an expensive piece of classic artwork. \\
+    20-22 & You win a magic item or an expensive piece of classic artwork. \\
+    23-24 & You win a magic item or an expensive piece of classic artwork. \\
+    25-26 & You win a magic item or an expensive piece of classic artwork. \\
+    27-28 & You win a magic item or an expensive piece of classic artwork. \\
+    29-30 & You win a magic item or an expensive piece of classic artwork. \\
+    31-32 & You win a magic item or an expensive piece of classic artwork. \\
+    33-34 & You win a magic item or an expensive piece of classic artwork. \\
+    35-36 & You win a magic item or an expensive piece of classic artwork. \\
+    37-38 & You win a magic item or an expensive piece of classic artwork. \\
+    39-40 & You win a magic item or an expensive piece of classic artwork. \\
+    41-42 & You win a magic item or an expensive piece of classic artwork. \\
+    43-44 & You win a magic item or an expensive piece of classic artwork. \\
+    45-46 & You win a magic item or an expensive piece of classic artwork. \\
+    47-48 & You win a magic item or an expensive piece of classic artwork. \\
+    49-50 & You win a magic item or an expensive piece of classic artwork. \\
+    51-52 & You win a magic item or an expensive piece of classic artwork. \\
+    53-54 & You win a magic item or an expensive piece of classic artwork. \\
+    55-56 & You win a magic item or an expensive piece of classic artwork. \\
+    57-58 & You win a magic item or an expensive piece of classic artwork. \\
+    59-60 & You win a magic item or an expensive piece of classic artwork. \\
+    61-62 & You win a magic item or an expensive piece of classic artwork. \\
+    63-64 & You win a magic item or an expensive piece of classic artwork. \\
+    65-66 & You win a magic item or an expensive piece of classic artwork. \\
+    67-68 & You win a magic item or an expensive piece of classic artwork. \\
+    69-70 & You win a magic item or an expensive piece of classic artwork. \\
+    71-72 & You win a magic item or an expensive piece of classic artwork. \\
+    73-74 & You win a magic item or an expensive piece of classic artwork. \\
+    75-76 & You win a magic item or an expensive piece of classic artwork. \\
+    77-78 & You win a magic item or an expensive piece of classic artwork. \\
+    79-80 & You win a magic item or an expensive piece of classic artwork. \\
+    81 & You win a magic item or an expensive piece of classic artwork. \\
+    82 & You win a magic item or an expensive piece of classic artwork. \\
+    83 & You win a magic item or an expensive piece of classic artwork. \\
+    84 & You win a magic item or an expensive piece of classic artwork. \\
+    85 & You win a magic item or an expensive piece of classic artwork. \\
+    86 & You win a magic item or an expensive piece of classic artwork. \\
+    87 & You win a magic item or an expensive piece of classic artwork. \\
+    88 & You win a magic item or an expensive piece of classic artwork. \\
+    89 & You win a magic item or an expensive piece of classic artwork. \\
+    90 & You win a magic item or an expensive piece of classic artwork. \\
+    91 & You win a magic item or an expensive piece of classic artwork. \\
+    92 & You win a magic item or an expensive piece of classic artwork. \\
+    93 & You win a magic item or an expensive piece of classic artwork. \\
+    94 & You win a magic item or an expensive piece of classic artwork. \\
+    95 & You win a magic item or an expensive piece of classic artwork. \\
+    96 & You win a magic item or an expensive piece of classic artwork. \\
+    97 & You win a magic item or an expensive piece of classic artwork. \\
+    98 & You win a magic item or an expensive piece of classic artwork. \\
+    99 & You win a magic item or an expensive piece of classic artwork. \\
+    100 & You win a magic item or an expensive piece of classic artwork. \\
+\end{dndlongtable}
+
+\subsection{Tables with Footnotes}
+
+\begin{minipage}{8cm}
+  \begin{DndTable}[header=Footnoted Table]{lX}
+    \textbf{Table head\footnote{\enspace Something to note}} & \textbf{Table head} \\
+    Some value  & Some value\footnote{\enspace Another thing to note} \\
+    Some value  & Some value \\
+    Some value  & Some value \\
+    Some value\footnote{\enspace The most important note}  & Some value \\
+  \end{DndTable}
+\end{minipage}
+
+\subsection{Ornamented Tables}
+The |ornamentedtabular| allows tables similar to those used for spellcasters
+(see over page).
+
+\begin{figure*}[h!]
+\begin{ornamentedtabular}{ccp{3.0cm}ccccccccccc}[title={The Full Caster}]
+  & & & & & \multicolumn{9}{c}{\thead{--- Spell Slots per Spell Level ---}} \\
+  \textbf{Level} & \textbf{\makecell{Proficiency\\Bonus}} & \textbf{Features} & \textbf{\makecell{Cantrips\\Known}} & \textbf{\makecell{Spells\\Known}} & \textbf{1st} & \textbf{2nd} & \textbf{3rd} & \textbf{4th} & \textbf{5th} & \textbf{6th} & \textbf{7th} & \textbf{8th} & \textbf{9th} \\
+  1st  & +2 & Feature & 3 & 4  & 2 & — & — & — & — & — & — & — & — \\
+  2nd  & +2 & Feature & 3 & 4  & 3 & — & — & — & — & — & — & — & — \\
+  3rd  & +2 & Feature & 3 & 4  & 4 & 2 & — & — & — & — & — & — & — \\
+  4th  & +2 & Feature & 4 & 5  & 4 & 3 & — & — & — & — & — & — & — \\
+  5th  & +3 & Feature & 4 & 6  & 4 & 3 & 2 & — & — & — & — & — & — \\
+  6th  & +3 & Feature & 4 & 7  & 4 & 3 & 3 & — & — & — & — & — & — \\
+  7th  & +3 & Feature & 4 & 8  & 4 & 3 & 3 & 1 & — & — & — & — & — \\
+  8th  & +3 & Feature & 4 & 9  & 4 & 3 & 3 & 2 & — & — & — & — & — \\
+  9th  & +4 & Feature & 4 & 10 & 4 & 3 & 3 & 3 & 1 & — & — & — & — \\
+  10th & +4 & Feature & 5 & 11 & 4 & 3 & 3 & 3 & 2 & — & — & — & — \\
+  11th & +4 & Feature & 5 & 12 & 4 & 3 & 3 & 3 & 2 & 1 & — & — & — \\
+  12th & +4 & Feature & 5 & 12 & 4 & 3 & 3 & 3 & 2 & 1 & — & — & — \\
+  13th & +5 & Feature & 5 & 13 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & — & — \\
+  14th & +5 & Feature & 5 & 13 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & — & — \\
+  15th & +5 & Feature & 5 & 14 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & — \\
+  16th & +5 & Feature & 5 & 14 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & — \\
+  17th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & 1 \\
+  18th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 1 & 1 & 1 & 1 \\
+  19th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 2 & 1 & 1 & 1 \\
+  20th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 2 & 2 & 1 & 1 \\
+\end{ornamentedtabular}
+\end{figure*}
 

### 2020-12-22 example.tex
Moved the "alternate" table examples over to the core example.tex file

@@
 \usepackage{stfloats}
-\usepackage{lmodern} % Scalable font
-\usepackage{lettrine} % For the drop cap
 \usetikzlibrary{intersections} % Required for ornamentedtabular
@@
 \begin{DndTable}[color=PhbLightCyan]{cX}
-  d8 & Item \\
+  \textbf{d8} & \textbf{Item} \\
   1 & Small wooden button \\
@@
   4 & Vial of green liquid \\
-  5  & Loaded dice \\
   6 & Tasty biscuit \\

### 2020-12-22 article.tex
Added example table stuff and complex theme color settings stuff to article.tex

@@
 \usepackage{titling}
+\usetikzlibrary{intersections} % Required for ornamentedtabular
 
@@
 % Note that the paper (\SetPaperImage) and footerscroll.pdf will probably need
-% to be modified for any % major color scheme change. The values below are
+% to be modified for any major color scheme change. The values below are
 % thematic for a sourcebook like GoS.
@@
 
-\subsection{Tables}
+\section{Tables}
+
+\subsection{Regular Table}
+
 The |DndTable| colors the even rows and is set to the width of a line by default.
@@
 
-\begin{lstlisting}
+\begin{lstlisting}[basicstyle=\ttfamily\small]
 \begin{DndTable}[cX][PhbLightCyan]
@@
 
-\begin{lstlisting}
+\begin{lstlisting}[basicstyle=\ttfamily\small]
 \begingroup
@@
 
+\subsection{More Theme Colors Control}
+Use |\DndSetComplexThemeColor| in order to have more precise control over the various theme colors defined within the document class.
+This command takes seven (7) |<color>| values that map to the following color variables within the theme:
+
+\begin{DndTable}[header=Complex Theme Parameter Map]{cX}
+  \textbf{Param \#} & \textbf{Variable Mapping} \\
+  1 & \textit{themecolor}, \textit{tablecolor} \\
+  2 & \textit{commentcolor}, \textit{sidebarcolor} \\
+  3 & \textit{readaloudcolor} (DndReadAloud background) \\
+  4 & \textit{readaloudbordercolor} \\
+  5 & \textit{titlecolor} \\
+  6 & \textit{titlerulecolor} \\
+  7 & \textit{pagecolor} (page numbers and footer) \\
+\end{DndTable}
+
+\begin{DndComment}{Note On Changing Schemes}
+If a major color scheme change is attempted, it is
+likely that the background ``paper'' (which can be overridden with
+|\SetPaperImage|) and footerscroll.pdf will need
+to be modified as well in order to fit the other color modifications.
+\end{DndComment}
+
+An example of these settings for a theme similar to the \textit{Ghosts of Saltmarsh} sourcebook:
+
+\begin{lstlisting}[basicstyle=\ttfamily\small]
+\definecolor {mytheme} {HTML} {DCF1E5}
+\definecolor {mysidebar} {HTML} {E9F5F5}
+\definecolor {myreadaloud} {HTML} {DCF1E5}
+\definecolor {myreadaloudborder} {HTML} {8AA7A2}
+\definecolor {mypagenum} {HTML} {B5D4CF}
+\DndSetComplexThemeColor[mytheme][mysidebar][myreadaloud][myreadaloudborder][titlered][titlegold][mypagenum]
+\end{lstlisting}
+
 \end{document}

### 2020-12-22 article.tex
Tweaks to the article.tex description of setting full color scheme values

@@
 
-\subsection{More Theme Colors Control}
+\subsection{Extra Theme Color Control}
 Use |\DndSetComplexThemeColor| in order to have more precise control over the various theme colors defined within the document class.
@@
 
-\begin{DndTable}[header=Complex Theme Parameter Map]{cX}
-  \textbf{Param \#} & \textbf{Variable Mapping} \\
-  1 & \textit{themecolor}, \textit{tablecolor} \\
-  2 & \textit{commentcolor}, \textit{sidebarcolor} \\
-  3 & \textit{readaloudcolor} (DndReadAloud background) \\
-  4 & \textit{readaloudbordercolor} \\
-  5 & \textit{titlecolor} \\
-  6 & \textit{titlerulecolor} \\
-  7 & \textit{pagecolor} (page numbers and footer) \\
+\begin{DndTable}[header=Complex Theme Parameter Map]{clX}
+  \textbf{\#} & \textbf{Variable Set} & \textbf{Affected Style} \\
+  1 & \textit{themecolor} & Used in |DndSetThemeColor|, set for future compatibility \\
+    & \textit{tablecolor} & |DndTable| \\
+  2 & \textit{commentcolor} & |DndComment| \\
+    & \textit{sidebarcolor} & |DndSidebar| \\
+  3 & \textit{readaloudcolor} & |DndReadAloud| background \\
+  4 & \textit{readaloudbordercolor} & |DndReadAloud| border \\
+  5 & \textit{titlecolor} & Titles of sections (|section|, |subsection|, etc) \\
+  6 & \textit{titlerulecolor} & |subsection| title ruling \\
+  7 & \textit{pagecolor} & Page numbers and footer \\
 \end{DndTable}
@@
 
-An example of these settings for a theme similar to the \textit{Ghosts of Saltmarsh} sourcebook:
+An example of these settings for a theme similar to the \textit{Ghosts of Saltmarsh} sourcebook.
+Note that the values for \textit{titlered} and \textit{titlegold} are used for the title and title rule colours unchanged in this example.
 

### 2020-12-23 article.tex
Added example colours to table in article.tex

@@
 \begin{table*}[b]%
-  \caption{}\label{tab:colors}
-
   \begin{DndTable}[width=\linewidth,header=Colors Supported by This Package]{lX}
     \textbf{Color}                  & \textbf{Description} \\
+    \rowcolor{PhbLightGreen}
     |PhbLightGreen|                 & Light green used in PHB Part 1 (Default) \\
+    \rowcolor{PhbLightCyan}
     |PhbLightCyan|                  & Light cyan used in PHB Part 2 \\
+    \rowcolor{PhbMauve}
     |PhbMauve|                      & Pale purple used in PHB Part 3 \\
+    \rowcolor{PhbTan}
     |PhbTan|                        & Light brown used in PHB appendix \\
+    \rowcolor{DmgLavender}
     |DmgLavender|                   & Pale purple used in DMG Part 1 \\
+    \rowcolor{DmgCoral}
     |DmgCoral|                      & Orange-pink used in DMG Part 2 \\
+    \rowcolor{DmgSlateGray}
     |DmgSlateGray| (|DmgSlateGrey|) & Blue-gray used in PHB Part 3 \\
+    \rowcolor{DmgLilac}
     |DmgLilac|                      & Purple-gray used in DMG appendix \\
+    \rowcolor{BrGreen}
+    |BrGreen|                       & Gray-green used for tables in Basic Rules\\
   \end{DndTable}

### 2020-12-23 example.tex
Added an example of the DndMonster stat block formatted in vertical (single-column) layout
Tweaked the complex colour setting function to allow comment and sidebar to have different colours

--- 2020-12-22 example.tex
@@
 % Monster stat block
+\begin{DndMonster}[float=t]{Monster Foo}
+  \DndMonsterType{Medium aberration (metasyntactic variable), neutral evil}
+
+  % If you want to use commas in the key values, enclose the values in braces.
+  \DndMonsterBasics[
+      armor-class = {9 (12 with \emph{mage armor})},
+      hit-points  = {\DndDice{3d8 + 3}},
+      speed       = {30 ft., fly 30 ft.},
+    ]
+
+  \DndMonsterAbilityScores[
+      str = 12,
+      dex = 8,
+      con = 13,
+      int = 10,
+      wis = 14,
+      cha = 15,
+    ]
+
+  \DndMonsterDetails[
+      %saving-throws = {Str +0, Dex +0, Con +0, Int +0, Wis +0, Cha +0},
+      %skills = {Acrobatics +0, Animal Handling +0, Arcana +0, Athletics +0, Deception +0, History +0, Insight +0, Intimidation +0, Investigation +0, Medicine +0, Nature +0, Perception +0, Performance +0, Persuasion +0, Religion +0, Sleight of Hand +0, Stealth +0, Survival +0},
+      %damage-vulnerabilities = {cold},
+      %damage-resistances = {bludgeoning, piercing, and slashing from nonmagical attacks},
+      %damage-immunities = {poison},
+      %condition-immunities = {poisoned},
+      senses = {darkvision 60 ft., passive Perception 10},
+      languages = {Common, Goblin, Undercommon},
+      challenge = 1,
+    ]
+  % Traits
+  \DndMonsterAction{Innate Spellcasting}
+  Foo's spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It can innately cast the following spells, requiring no material components:
+  \begin{DndMonsterSpells}
+    \DndInnateSpellLevel{misty step}
+    \DndInnateSpellLevel[3]{fog cloud, rope trick}
+    \DndInnateSpellLevel[1]{identify}
+  \end{DndMonsterSpells}
+
+  \DndMonsterAction{Spellcasting}
+  Foo is a 2nd-level spellcaster. Its spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It has the following sorcerer spells prepared:
+  \begin{DndMonsterSpells}
+    \DndMonsterSpellLevel{blade ward, fire bolt, light, shocking grasp}
+    \DndMonsterSpellLevel[1][3]{burning hands, mage armor, shield}
+  \end{DndMonsterSpells}
+
+  \DndMonsterSection{Actions}
+  \DndMonsterAction{Multiattack}
+  The foo makes two melee attacks.
+
+  %Default values are shown commented out
+  \DndMonsterAttack[
+    name=Dagger,
+    %distance=both, % valid options are in the set {both,melee,ranged},
+    %type=weapon, %valid options are in the set {weapon,spell}
+    mod=+3,
+    %reach=5,
+    %range=20/60,
+    %targets=one target,
+    dmg=\DndDice{1d4+1},
+    dmg-type=piercing,
+    %plus-dmg=,
+    %plus-dmg-type=,
+    %or-dmg=,
+    %or-dmg-when=,
+    %extra=,
+  ]
+
+  %\DndMonsterMelee calls \DndMonsterAttack with the melee option
+  \DndMonsterMelee[
+    name=Flame Tongue Longsword,
+    mod=+3,
+    %reach=5,
+    %targets=one target,
+    dmg=\DndDice{1d8+1},
+    dmg-type=slashing,
+    plus-dmg=\DndDice{2d6},
+    plus-dmg-type=fire,
+    or-dmg=\DndDice{1d10+1},
+    or-dmg-when=if used with two hands,
+    %extra=,
+  ]
+
+  %\DndMonsterRanged calls \DndMonsterAttack with the ranged option
+  \DndMonsterRanged[
+    name=Assassin's Light Crossbow,
+    mod=+1,
+    range=80/320,
+    dmg=\DndDice{1d8},
+    dmg-type=piercing,
+    %plus-dmg=,
+    %plus-dmg-type=,
+    %or-dmg=,
+    %or-dmg-when=,
+    extra={, and the target must make a DC 15 Constitution saving throw, taking 24 (7d6) poison damage on a failed save, or half as much damage on a successful one}
+  ]
+
+  % Legendary Actions
+  \DndMonsterSection{Legendary Actions}
+  The foo can take 3 legendary actions, choosing from the options below.
+Only one legendary action option can be used at a time and only at the end of another creature's turn.
+The foo regains spent legendary actions at the start of its turn.
+
+  \begin{DndMonsterLegendaryActions}
+    \DndMonsterLegendaryAction{Move}{The foo moves up to its speed.}
+    \DndMonsterLegendaryAction{Dagger Attack}{The foo makes a dagger attack.}
+    \DndMonsterLegendaryAction{Create Contract (Costs 3 Actions)}{The foo presents a contract in a language it knows and waves it in the face of a creature within 10 feet.
+The creature must make a DC 10 Intelligence saving throw.
+On a failure, the creature is incapacitated until the start of the foo's next turn.
+A creature who cannot read the language in which the contract is written has advantage on this saving throw.}
+  \end{DndMonsterLegendaryActions}
+\end{DndMonster}
+
+% Monster stat block
 \begin{DndMonster}[float*=b,width=\textwidth + 8pt]{Monster Foo}
@@
 
-The |DndMonster| environment is used to typeset monster and NPC stat blocks. The module supplies many functions to easily typeset the contents of the stat block
+The |DndMonster| environment is used to typeset monster and NPC stat blocks. The module supplies many functions to easily typeset the contents of the stat block.
+
+The stat block can be formatted either as a single column, or as a block that spans the page horizontally.
 
@@
 
+\subsection{Extra Theme Color Control}
+Use |\DndSetComplexThemeColor| in order to have more precise control over the various theme colors defined within the document class.
+This command takes eight (8) |<color>| values that map to the following color variables within the theme:
+
+\begin{DndTable}[header=Complex Theme Parameter Map]{clX}
+  \textbf{\#} & \textbf{Variable Set} & \textbf{Affected Style} \\
+  1 & \textit{themecolor} & Used in |DndSetThemeColor|; set for future compatibility \\
+    & \textit{tablecolor} & |DndTable| \\
+  2 & \textit{commentcolor} & |DndComment| \\
+  3 & \textit{sidebarcolor} & |DndSidebar| \\
+  4 & \textit{readaloudcolor} & |DndReadAloud| background \\
+  5 & \textit{readaloudbordercolor} & |DndReadAloud| border \\
+  6 & \textit{titlecolor} & Titles of sections (|section|, |subsection|, etc) \\
+  7 & \textit{titlerulecolor} & |subsection| title ruling \\
+  8 & \textit{pagecolor} & Page numbers and footer \\
+\end{DndTable}
+
+\begin{DndComment}{Note On Changing Schemes}
+If a major color scheme change is attempted, it is
+likely that the background ``paper'' (which can be overridden with
+|\SetPaperImage|) and footerscroll.pdf will need
+to be modified as well in order to fit the other color modifications.
+\end{DndComment}
+
+An example of these settings for a theme similar to the \textit{Ghosts of Saltmarsh} sourcebook.
+Note that the values for \textit{titlered} and \textit{titlegold} are used for the title and title rule colours unchanged in this example.
+
+\begin{lstlisting}[basicstyle=\ttfamily\small]
+\definecolor {mytheme} {HTML} {DCF1E5}
+\definecolor {mycomment} {HTML} {E9F5F5}
+\definecolor {mysidebar} {HTML} {E9F5F5}
+\definecolor {myreadaloud} {HTML} {DCF1E5}
+\definecolor {myreadaloudborder} {HTML} {8AA7A2}
+\definecolor {mypagenum} {HTML} {B5D4CF}
+\DndSetComplexThemeColor[mytheme][mycomment][mysidebar][myreadaloud][myreadaloudborder][titlered][titlegold][mypagenum]
+\end{lstlisting}
+
 \end{document}

### 2020-12-23 article.tex
Tweaked the complex colour setting function to allow comment and sidebar to have different colours

@@
 \definecolor {mytheme}      {HTML} {DCF1E5} %
+\definecolor {mycomment}    {HTML} {E9F5F5} %
 \definecolor {mysidebar}    {HTML} {E9F5F5} %
@@
 \definecolor {mypagenum}  {HTML} {B5D4CF} %
-%\DndSetComplexThemeColor[mytheme][mysidebar][myreadaloud][myreadaloudborder][titlered][titlegold][mypagenum]
+%\DndSetComplexThemeColor[mytheme][mycomment][mysidebar][myreadaloud][myreadaloudborder][titlered][titlegold][mypagenum]
 
@@
 Use |\DndSetComplexThemeColor| in order to have more precise control over the various theme colors defined within the document class.
-This command takes seven (7) |<color>| values that map to the following color variables within the theme:
+This command takes eight (8) |<color>| values that map to the following color variables within the theme:
 
@@
   \textbf{\#} & \textbf{Variable Set} & \textbf{Affected Style} \\
-  1 & \textit{themecolor} & Used in |DndSetThemeColor|, set for future compatibility \\
+  1 & \textit{themecolor} & Used in |DndSetThemeColor|; set for future compatibility \\
     & \textit{tablecolor} & |DndTable| \\
   2 & \textit{commentcolor} & |DndComment| \\
-    & \textit{sidebarcolor} & |DndSidebar| \\
-  3 & \textit{readaloudcolor} & |DndReadAloud| background \\
-  4 & \textit{readaloudbordercolor} & |DndReadAloud| border \\
-  5 & \textit{titlecolor} & Titles of sections (|section|, |subsection|, etc) \\
-  6 & \textit{titlerulecolor} & |subsection| title ruling \\
-  7 & \textit{pagecolor} & Page numbers and footer \\
+  3 & \textit{sidebarcolor} & |DndSidebar| \\
+  4 & \textit{readaloudcolor} & |DndReadAloud| background \\
+  5 & \textit{readaloudbordercolor} & |DndReadAloud| border \\
+  6 & \textit{titlecolor} & Titles of sections (|section|, |subsection|, etc) \\
+  7 & \textit{titlerulecolor} & |subsection| title ruling \\
+  8 & \textit{pagecolor} & Page numbers and footer \\
 \end{DndTable}
@@
 \definecolor {mytheme} {HTML} {DCF1E5}
+\definecolor {mycomment} {HTML} {E9F5F5}
 \definecolor {mysidebar} {HTML} {E9F5F5}
@@
 \definecolor {mypagenum} {HTML} {B5D4CF}
-\DndSetComplexThemeColor[mytheme][mysidebar][myreadaloud][myreadaloudborder][titlered][titlegold][mypagenum]
+\DndSetComplexThemeColor[mytheme][mycomment][mysidebar][myreadaloud][myreadaloudborder][titlered][titlegold][mypagenum]
 \end{lstlisting}

### 2020-12-23 example.tex
Set size of the tt example code blocks to small to try and fit a bit better in a column
Made reference to footerscroll.pdf file fixed width font

--- 2020-12-23 example.tex
@@
 
-\begin{lstlisting}
+\begin{lstlisting}[basicstyle=\ttfamily\small]
 \begin{DndTable}[color=PhbLightCyan]{cX}
@@
 likely that the background ``paper'' (which can be overridden with
-|\SetPaperImage|) and footerscroll.pdf will need
+|\SetPaperImage|) and |footerscroll.pdf| will need
 to be modified as well in order to fit the other color modifications.

### 2020-12-24 example.tex
Fixed typo in supported colors table, DmgSlateGray referncing PHB instead of DMB
Added note on how to achieve the "footnoted table" effect

@@
 \subsection{Tables with Footnotes}
+Surrounding one of the existing table types with a |minipage| section
+allows footnotes declared in the table to appear at the end of the table,
+rather than in the page footer as normal. For a regularly sized table
+in the two-column layout, the following declaration can be used:
+
+\begin{lstlisting}[basicstyle=\ttfamily\small]
+\begin{minipage}{8cm}
+  \begin{DndTable}
+    ...
+    ...
+  \end{DndTable}
+\end{minipage}
+\end{lstlisting}
+
+To achieve the following effect:
 
@@
     \rowcolor{DmgSlateGray}
-    |DmgSlateGray| (|DmgSlateGrey|) & Blue-gray used in PHB Part 3 \\
+    |DmgSlateGray| (|DmgSlateGrey|) & Blue-gray used in DMG Part 3 \\
     \rowcolor{DmgLilac}

### 2021-01-04 example.tex
New command \tocside adds sidebar entry to table of contents

--- 2020-12-23 example.tex
@@
 \usepackage{stfloats}
-\usetikzlibrary{intersections} % Required for ornamentedtabular
 
 \captionsetup[table]{labelformat=empty,font={sf,sc,bf,},skip=0pt}
-
-% Uncomment to allow the default background paper image to be overridden.
-%\SetPaperImage{img/paper}
 
@@
 
-\section{Alternate Map Region Styles}
-Published modules sometimes use plain numbers for locations, sometimes plain
-letters, and sometimes they prefix a character to the front of the numbers.
-The following options can be used to display in these forms:
-
-\numberedarea{Numbered Dungeon}
-Areas in the Numbered Dungeon have sequential numbers. This is done using
-the following commands:
-
-\begin{verbatim}
-\numberedarea{Numbered Dungeon}
-\numberedsubarea{Entry}
-\numberedsubarea{Trap}
-\numberedsubarea{Fight}
-\numberedsubarea{Exit}
-\end{verbatim}
-
-These commands yield the following results:
-\numberedsubarea{Entry}
-\numberedsubarea{Trap}
-\numberedsubarea{Fight}
-\numberedsubarea{Exit}
-
-\letteredarea{Lettered Dungeon}
-Areas in the Lettered Dungeon are labelled with sequential characters
-(A, B, C, etc). This is done using the following commands:
-
-\begin{verbatim}
-\letteredarea{Lettered Dungeon}
-\letteredsubarea{Entry}
-\letteredsubarea{Trap}
-\letteredsubarea{Fight}
-\letteredsubarea{Exit}
-\end{verbatim}
-
-These commands yield the following results:
-\letteredsubarea{Entry}
-\letteredsubarea{Trap}
-\letteredsubarea{Fight}
-\letteredsubarea{Exit}
-
-\prefixedarea{Prefixed Dungeon}{Z}
-Areas in the Prefixed Dungeon have a custom prefix character,
-in this case: `\prefixedareaprefix'.
-This is done using the following commands:
-
-\begin{verbatim}
-\prefixedarea{Prefixed Dungeon}{Z}
-\prefixedsubarea{Entry}
-\prefixedsubarea{Trap}
-\prefixedsubarea{Fight}
-\prefixedsubarea{Exit}
-\end{verbatim}
-
-These commands yield the following results:
-\prefixedsubarea{Entry}
-\prefixedsubarea{Trap}
-\prefixedsubarea{Fight}
-\prefixedsubarea{Exit}
-
 \chapter{Text Boxes}
@@
 \begin{DndSidebar}[float=!b]{Behold the DndSidebar!}
+\tocside{Behold the DndSidebar!}
   The |DndSidebar| is used as a sidebar.
 It does not break over columns and is best used with a figure environment to float it to one corner of the page where the surrounding text can then flow around it.
+
+  Use the |\tocside{title}| command to create an entry in the table of contents, if you want.
 \end{DndSidebar}
@@
 \section{Tables}
-
-\subsection{Regular Table}
 The |DndTable| colors the even rows and is set to the width of a line by default.
@@
 
-\subsection{Alternate Table Background}
-
-The |DndAltTable| allows tables that have a blank "header" line followed
-by alternating theme color and white background, as per some of the sourcebooks.
-
-\begin{DndAltTable}{cX}
-    \textbf{Table head} & \textbf{Table head} \\
-    Some value  & Some value \\
-    Some value  & Some value \\
-    Some value  & Some value \\
-    Some value  & Some value \\
-\end{DndAltTable}
-
-\subsection{Long Table that Spans Pages}
-
-The |dndlongtable| allows table that can span multiple pages. The current
-version is configured to do a two-column table.
-
-\begin{dndlongtable}
-    \textbf{Roll (d100)} & \textbf{Result} \\
-    1-2 & You win a magic item or an expensive piece of classic artwork. \\
-    3-4 & You win a magic item or an expensive piece of classic artwork. \\
-    5-6 & You win a magic item or an expensive piece of classic artwork. \\
-    7-8 & You win a magic item or an expensive piece of classic artwork. \\
-    9-10 & You win a magic item or an expensive piece of classic artwork. \\
-    11-12 & You win a magic item or an expensive piece of classic artwork. \\
-    13-14 & You win a magic item or an expensive piece of classic artwork. \\
-    15-16 & You win a magic item or an expensive piece of classic artwork. \\
-    17-18 & You win a magic item or an expensive piece of classic artwork. \\
-    19-20 & You win a magic item or an expensive piece of classic artwork. \\
-    20-22 & You win a magic item or an expensive piece of classic artwork. \\
-    23-24 & You win a magic item or an expensive piece of classic artwork. \\
-    25-26 & You win a magic item or an expensive piece of classic artwork. \\
-    27-28 & You win a magic item or an expensive piece of classic artwork. \\
-    29-30 & You win a magic item or an expensive piece of classic artwork. \\
-    31-32 & You win a magic item or an expensive piece of classic artwork. \\
-    33-34 & You win a magic item or an expensive piece of classic artwork. \\
-    35-36 & You win a magic item or an expensive piece of classic artwork. \\
-    37-38 & You win a magic item or an expensive piece of classic artwork. \\
-    39-40 & You win a magic item or an expensive piece of classic artwork. \\
-    41-42 & You win a magic item or an expensive piece of classic artwork. \\
-    43-44 & You win a magic item or an expensive piece of classic artwork. \\
-    45-46 & You win a magic item or an expensive piece of classic artwork. \\
-    47-48 & You win a magic item or an expensive piece of classic artwork. \\
-    49-50 & You win a magic item or an expensive piece of classic artwork. \\
-    51-52 & You win a magic item or an expensive piece of classic artwork. \\
-    53-54 & You win a magic item or an expensive piece of classic artwork. \\
-    55-56 & You win a magic item or an expensive piece of classic artwork. \\
-    57-58 & You win a magic item or an expensive piece of classic artwork. \\
-    59-60 & You win a magic item or an expensive piece of classic artwork. \\
-    61-62 & You win a magic item or an expensive piece of classic artwork. \\
-    63-64 & You win a magic item or an expensive piece of classic artwork. \\
-    65-66 & You win a magic item or an expensive piece of classic artwork. \\
-    67-68 & You win a magic item or an expensive piece of classic artwork. \\
-    69-70 & You win a magic item or an expensive piece of classic artwork. \\
-    71-72 & You win a magic item or an expensive piece of classic artwork. \\
-    73-74 & You win a magic item or an expensive piece of classic artwork. \\
-    75-76 & You win a magic item or an expensive piece of classic artwork. \\
-    77-78 & You win a magic item or an expensive piece of classic artwork. \\
-    79-80 & You win a magic item or an expensive piece of classic artwork. \\
-    81 & You win a magic item or an expensive piece of classic artwork. \\
-    82 & You win a magic item or an expensive piece of classic artwork. \\
-    83 & You win a magic item or an expensive piece of classic artwork. \\
-    84 & You win a magic item or an expensive piece of classic artwork. \\
-    85 & You win a magic item or an expensive piece of classic artwork. \\
-    86 & You win a magic item or an expensive piece of classic artwork. \\
-    87 & You win a magic item or an expensive piece of classic artwork. \\
-    88 & You win a magic item or an expensive piece of classic artwork. \\
-    89 & You win a magic item or an expensive piece of classic artwork. \\
-    90 & You win a magic item or an expensive piece of classic artwork. \\
-    91 & You win a magic item or an expensive piece of classic artwork. \\
-    92 & You win a magic item or an expensive piece of classic artwork. \\
-    93 & You win a magic item or an expensive piece of classic artwork. \\
-    94 & You win a magic item or an expensive piece of classic artwork. \\
-    95 & You win a magic item or an expensive piece of classic artwork. \\
-    96 & You win a magic item or an expensive piece of classic artwork. \\
-    97 & You win a magic item or an expensive piece of classic artwork. \\
-    98 & You win a magic item or an expensive piece of classic artwork. \\
-    99 & You win a magic item or an expensive piece of classic artwork. \\
-    100 & You win a magic item or an expensive piece of classic artwork. \\
-\end{dndlongtable}
-
-\subsection{Tables with Footnotes}
-
-\begin{minipage}{8cm}
-  \begin{DndTable}[header=Footnoted Table]{lX}
-    \textbf{Table head\footnote{\enspace Something to note}} & \textbf{Table head} \\
-    Some value  & Some value\footnote{\enspace Another thing to note} \\
-    Some value  & Some value \\
-    Some value  & Some value \\
-    Some value\footnote{\enspace The most important note}  & Some value \\
-  \end{DndTable}
-\end{minipage}
-
-\subsection{Ornamented Tables}
-The |ornamentedtabular| allows tables similar to those used for spellcasters
-(see over page).
-
-\begin{figure*}[h!]
-\begin{ornamentedtabular}{ccp{3.0cm}ccccccccccc}[title={The Full Caster}]
-  & & & & & \multicolumn{9}{c}{\thead{--- Spell Slots per Spell Level ---}} \\
-  \textbf{Level} & \textbf{\makecell{Proficiency\\Bonus}} & \textbf{Features} & \textbf{\makecell{Cantrips\\Known}} & \textbf{\makecell{Spells\\Known}} & \textbf{1st} & \textbf{2nd} & \textbf{3rd} & \textbf{4th} & \textbf{5th} & \textbf{6th} & \textbf{7th} & \textbf{8th} & \textbf{9th} \\
-  1st  & +2 & Feature & 3 & 4  & 2 & — & — & — & — & — & — & — & — \\
-  2nd  & +2 & Feature & 3 & 4  & 3 & — & — & — & — & — & — & — & — \\
-  3rd  & +2 & Feature & 3 & 4  & 4 & 2 & — & — & — & — & — & — & — \\
-  4th  & +2 & Feature & 4 & 5  & 4 & 3 & — & — & — & — & — & — & — \\
-  5th  & +3 & Feature & 4 & 6  & 4 & 3 & 2 & — & — & — & — & — & — \\
-  6th  & +3 & Feature & 4 & 7  & 4 & 3 & 3 & — & — & — & — & — & — \\
-  7th  & +3 & Feature & 4 & 8  & 4 & 3 & 3 & 1 & — & — & — & — & — \\
-  8th  & +3 & Feature & 4 & 9  & 4 & 3 & 3 & 2 & — & — & — & — & — \\
-  9th  & +4 & Feature & 4 & 10 & 4 & 3 & 3 & 3 & 1 & — & — & — & — \\
-  10th & +4 & Feature & 5 & 11 & 4 & 3 & 3 & 3 & 2 & — & — & — & — \\
-  11th & +4 & Feature & 5 & 12 & 4 & 3 & 3 & 3 & 2 & 1 & — & — & — \\
-  12th & +4 & Feature & 5 & 12 & 4 & 3 & 3 & 3 & 2 & 1 & — & — & — \\
-  13th & +5 & Feature & 5 & 13 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & — & — \\
-  14th & +5 & Feature & 5 & 13 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & — & — \\
-  15th & +5 & Feature & 5 & 14 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & — \\
-  16th & +5 & Feature & 5 & 14 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & — \\
-  17th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & 1 \\
-  18th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 1 & 1 & 1 & 1 \\
-  19th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 2 & 1 & 1 & 1 \\
-  20th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 2 & 2 & 1 & 1 \\
-\end{ornamentedtabular}
-\end{figure*}
-
 \chapter{Monsters and NPCs}
-
-% Monster stat block
-\begin{DndMonster}[float=t]{Monster Foo}
-  \DndMonsterType{Medium aberration (metasyntactic variable), neutral evil}
-
-  % If you want to use commas in the key values, enclose the values in braces.
-  \DndMonsterBasics[
-      armor-class = {9 (12 with \emph{mage armor})},
-      hit-points  = {\DndDice{3d8 + 3}},
-      speed       = {30 ft., fly 30 ft.},
-    ]
-
-  \DndMonsterAbilityScores[
-      str = 12,
-      dex = 8,
-      con = 13,
-      int = 10,
-      wis = 14,
-      cha = 15,
-    ]
-
-  \DndMonsterDetails[
-      %saving-throws = {Str +0, Dex +0, Con +0, Int +0, Wis +0, Cha +0},
-      %skills = {Acrobatics +0, Animal Handling +0, Arcana +0, Athletics +0, Deception +0, History +0, Insight +0, Intimidation +0, Investigation +0, Medicine +0, Nature +0, Perception +0, Performance +0, Persuasion +0, Religion +0, Sleight of Hand +0, Stealth +0, Survival +0},
-      %damage-vulnerabilities = {cold},
-      %damage-resistances = {bludgeoning, piercing, and slashing from nonmagical attacks},
-      %damage-immunities = {poison},
-      %condition-immunities = {poisoned},
-      senses = {darkvision 60 ft., passive Perception 10},
-      languages = {Common, Goblin, Undercommon},
-      challenge = 1,
-    ]
-  % Traits
-  \DndMonsterAction{Innate Spellcasting}
-  Foo's spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It can innately cast the following spells, requiring no material components:
-  \begin{DndMonsterSpells}
-    \DndInnateSpellLevel{misty step}
-    \DndInnateSpellLevel[3]{fog cloud, rope trick}
-    \DndInnateSpellLevel[1]{identify}
-  \end{DndMonsterSpells}
-
-  \DndMonsterAction{Spellcasting}
-  Foo is a 2nd-level spellcaster. Its spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It has the following sorcerer spells prepared:
-  \begin{DndMonsterSpells}
-    \DndMonsterSpellLevel{blade ward, fire bolt, light, shocking grasp}
-    \DndMonsterSpellLevel[1][3]{burning hands, mage armor, shield}
-  \end{DndMonsterSpells}
-
-  \DndMonsterSection{Actions}
-  \DndMonsterAction{Multiattack}
-  The foo makes two melee attacks.
-
-  %Default values are shown commented out
-  \DndMonsterAttack[
-    name=Dagger,
-    %distance=both, % valid options are in the set {both,melee,ranged},
-    %type=weapon, %valid options are in the set {weapon,spell}
-    mod=+3,
-    %reach=5,
-    %range=20/60,
-    %targets=one target,
-    dmg=\DndDice{1d4+1},
-    dmg-type=piercing,
-    %plus-dmg=,
-    %plus-dmg-type=,
-    %or-dmg=,
-    %or-dmg-when=,
-    %extra=,
-  ]
-
-  %\DndMonsterMelee calls \DndMonsterAttack with the melee option
-  \DndMonsterMelee[
-    name=Flame Tongue Longsword,
-    mod=+3,
-    %reach=5,
-    %targets=one target,
-    dmg=\DndDice{1d8+1},
-    dmg-type=slashing,
-    plus-dmg=\DndDice{2d6},
-    plus-dmg-type=fire,
-    or-dmg=\DndDice{1d10+1},
-    or-dmg-when=if used with two hands,
-    %extra=,
-  ]
-
-  %\DndMonsterRanged calls \DndMonsterAttack with the ranged option
-  \DndMonsterRanged[
-    name=Assassin's Light Crossbow,
-    mod=+1,
-    range=80/320,
-    dmg=\DndDice{1d8},
-    dmg-type=piercing,
-    %plus-dmg=,
-    %plus-dmg-type=,
-    %or-dmg=,
-    %or-dmg-when=,
-    extra={, and the target must make a DC 15 Constitution saving throw, taking 24 (7d6) poison damage on a failed save, or half as much damage on a successful one}
-  ]
-
-  % Legendary Actions
-  \DndMonsterSection{Legendary Actions}
-  The foo can take 3 legendary actions, choosing from the options below.
-Only one legendary action option can be used at a time and only at the end of another creature's turn.
-The foo regains spent legendary actions at the start of its turn.
-
-  \begin{DndMonsterLegendaryActions}
-    \DndMonsterLegendaryAction{Move}{The foo moves up to its speed.}
-    \DndMonsterLegendaryAction{Dagger Attack}{The foo makes a dagger attack.}
-    \DndMonsterLegendaryAction{Create Contract (Costs 3 Actions)}{The foo presents a contract in a language it knows and waves it in the face of a creature within 10 feet.
-The creature must make a DC 10 Intelligence saving throw.
-On a failure, the creature is incapacitated until the start of the foo's next turn.
-A creature who cannot read the language in which the contract is written has advantage on this saving throw.}
-  \end{DndMonsterLegendaryActions}
-\end{DndMonster}
 
@@
 
-The |DndMonster| environment is used to typeset monster and NPC stat blocks. The module supplies many functions to easily typeset the contents of the stat block.
-
-The stat block can be formatted either as a single column, or as a block that spans the page horizontally.
+The |DndMonster| environment is used to typeset monster and NPC stat blocks. The module supplies many functions to easily typeset the contents of the stat block
 
@@
 
-\begin{lstlisting}[basicstyle=\ttfamily\small]
+\begin{lstlisting}
 \begin{DndTable}[color=PhbLightCyan]{cX}
@@
 
-\begin{lstlisting}[basicstyle=\ttfamily\small]
+\begin{lstlisting}
 \begingroup
@@
 
-\subsection{Extra Theme Color Control}
-Use |\DndSetComplexThemeColor| in order to have more precise control over the various theme colors defined within the document class.
-This command takes eight (8) |<color>| values that map to the following color variables within the theme:
-
-\begin{DndTable}[header=Complex Theme Parameter Map]{clX}
-  \textbf{\#} & \textbf{Variable Set} & \textbf{Affected Style} \\
-  1 & \textit{themecolor} & Used in |DndSetThemeColor|; set for future compatibility \\
-    & \textit{tablecolor} & |DndTable| \\
-  2 & \textit{commentcolor} & |DndComment| \\
-  3 & \textit{sidebarcolor} & |DndSidebar| \\
-  4 & \textit{readaloudcolor} & |DndReadAloud| background \\
-  5 & \textit{readaloudbordercolor} & |DndReadAloud| border \\
-  6 & \textit{titlecolor} & Titles of sections (|section|, |subsection|, etc) \\
-  7 & \textit{titlerulecolor} & |subsection| title ruling \\
-  8 & \textit{pagecolor} & Page numbers and footer \\
-\end{DndTable}
-
-\begin{DndComment}{Note On Changing Schemes}
-If a major color scheme change is attempted, it is
-likely that the background ``paper'' (which can be overridden with
-|\SetPaperImage|) and |footerscroll.pdf| will need
-to be modified as well in order to fit the other color modifications.
-\end{DndComment}
-
-An example of these settings for a theme similar to the \textit{Ghosts of Saltmarsh} sourcebook.
-Note that the values for \textit{titlered} and \textit{titlegold} are used for the title and title rule colours unchanged in this example.
-
-\begin{lstlisting}[basicstyle=\ttfamily\small]
-\definecolor {mytheme} {HTML} {DCF1E5}
-\definecolor {mycomment} {HTML} {E9F5F5}
-\definecolor {mysidebar} {HTML} {E9F5F5}
-\definecolor {myreadaloud} {HTML} {DCF1E5}
-\definecolor {myreadaloudborder} {HTML} {8AA7A2}
-\definecolor {mypagenum} {HTML} {B5D4CF}
-\DndSetComplexThemeColor[mytheme][mycomment][mysidebar][myreadaloud][myreadaloudborder][titlered][titlegold][mypagenum]
-\end{lstlisting}
-
 \end{document}

### 2021-01-04 example.tex
New command \tocside adds sidebar entry to table of contents
Support for multiple maps using \DndMap{title} and \ref{map:title}

--- 2020-12-24 example.tex
@@
 
+The command |\DndMap{title}| creates a new map index (A, B, C\ldots).
+This doesn't add anything to the document, but the map index can be referenced with |\ref{map:title}|.
+For example, the Kingdom is map\,\ref{map:The Kingdom}.
+
+\DndMap{The Kingdom}
+
+Areas can be references with |\ref{area:name}|. For example, Mount Doofus is area \ref{area:Mount Doofus}.
+
 \DndArea{Village of Hommlet}
@@
 
+\section{Map References}
+
+\DndArea[\ref{map:The Kingdom}]{Mount Doofus}
+This area has a prefix before the number. The prefix is an optional parameter on |\DndArea|. Useful if your document contains multiple maps!
+
 \chapter{Text Boxes}

### 2021-01-04 example.tex
Support for multiple maps using \DndMap{title} and \ref{map:title}

--- 2021-01-04 example.tex
@@
 A five-foot hole reveals the dirt floor illuminated by a hole in the roof.
+
+\DndArea[\ref{map:The Kingdom}]{Mount Doofus}
+This area has a prefix before the number. The prefix is an optional parameter on |\DndArea|. Useful if your document contains multiple maps!
 

### 2021-01-05 example.tex
Improvements to map index referencing, and better appendix formatting in table of contents

@@
 
-\title{The Dark \LaTeX{} \\
-\large An Example of the dndbook Class}
-\author{The rpgTeX Team}
-\date{2020/04/21}
+\title{
+  \Huge \scshape \fontfamily{pbk}\selectfont
+  The Dark \LaTeX{} \\
+  \medskip
+  \normalfont
+  \large
+  An Example of the dndbook Class
+}
+\author{The rpgTeX Team \and Steve}
+\date{}
 
@@
 
-\DndArea[\ref{map:The Kingdom}]{Mount Doofus}
-This area has a prefix before the number. The prefix is an optional parameter on |\DndArea|. Useful if your document contains multiple maps!
+\DndArea[The Kingdom]{Mount Doofus}
+This area has a map reference before the number. The map name is an optional parameter on |\DndArea|. Useful if your document contains multiple maps!
 
@@
 
+\part{Appendices}
+
+\appendix
+
+\chapter{One Last Thing}
+
+\DndDropCapLine{U}sing the |\appendix| command causes all subsequent chapters to be formatted as appendices. Neat!
+
 \end{document}

### 2021-01-26 example.tex

@@
 
-\title{
-  \Huge \scshape \fontfamily{pbk}\selectfont
-  The Dark \LaTeX{} \\
-  \medskip
-  \normalfont
-  \large
-  An Example of the dndbook Class
-}
-\author{The rpgTeX Team \and Steve}
-\date{}
+\title{The Dark \LaTeX{} \\
+\large An Example of the dndbook Class}
+\author{The rpgTeX Team}
+\date{2020/04/21}
 
@@
 The map region functions |\DndArea| and |\DndSubArea| provide automatic numbering of areas.
-
-The command |\DndMap{title}| creates a new map index (A, B, C\ldots).
-This doesn't add anything to the document, but the map index can be referenced with |\ref{map:title}|.
-For example, the Kingdom is map\,\ref{map:The Kingdom}.
-
-\DndMap{The Kingdom}
-
-Areas can be references with |\ref{area:name}|. For example, Mount Doofus is area \ref{area:Mount Doofus}.
 
@@
 
-\section{Map References}
-
-\DndArea[The Kingdom]{Mount Doofus}
-This area has a map reference before the number. The map name is an optional parameter on |\DndArea|. Useful if your document contains multiple maps!
-
 \chapter{Text Boxes}
@@
 \begin{DndSidebar}[float=!b]{Behold the DndSidebar!}
-\tocside{Behold the DndSidebar!}
   The |DndSidebar| is used as a sidebar.
 It does not break over columns and is best used with a figure environment to float it to one corner of the page where the surrounding text can then flow around it.
-
-  Use the |\tocside{title}| command to create an entry in the table of contents, if you want.
 \end{DndSidebar}
@@
   4  & Vial of green liquid \\
-  5  & Loaded dice \\
   6  & Tasty biscuit \\
@@
 
-\part{Appendices}
-
-\appendix
-
-\chapter{One Last Thing}
-
-\DndDropCapLine{U}sing the |\appendix| command causes all subsequent chapters to be formatted as appendices. Neat!
-
 \end{document}

### 2021-06-18 example.tex
Added optional Proficiency Bonus modifier on the same line (right justified) as the Challenge rating. Proficiency is a string, so values such as "equals your bonus" can be used.

@@
 \usepackage{stfloats}
+\usepackage{lmodern} % Scalable font
+\usepackage{lettrine} % For the drop cap
 \usetikzlibrary{intersections} % Required for ornamentedtabular
@@
       languages = {Common, Goblin, Undercommon},
-      challenge = 1,
+      challenge = ---,
+      proficiency = equals your bonus
     ]
@@
         challenge = 1,
+        %proficiency = +2,
       ]

### 2021-06-29 article.tex
Fixed typo in supported colors table, DmgSlateGray referncing PHB instead of DMG
Updated article.tex to include the usage for optional table header row boldface

@@
 \end{DndTable}
+
+The text in the first row of the table automatically uses boldface;
+to prevent this, add ``bold=false'' to the optional parameters, for example:
+\begin{lstlisting}[basicstyle=\ttfamily\small]
+[header=Nice Table,bold=false]
+\end{lstlisting}
 
@@
 
-\begin{DndAltTable}{cX}
+\begin{DndAltTable}[header=Alternate Table,bold=false]{cX}
     \textbf{Table head} & \textbf{Table head} \\

### 2021-07-07 article.tex
Mirror gryphius' fix for entry 5 in the d8 table example in article.tex as well.

@@
   4           & Vial of green liquid \\
+  5           & Loaded dice \\
   6           & Tasty biscuit \\

### 2021-07-11 example.tex
Added an option to prevent the automatic boldface of table first row text; default is still true.
Added the option to avoid boldface table header row in the DndAltTable
Added a "listparagraph" type that outputs a bolded title with hanging-indent text, used in class features, background options, etc

--- 2021-06-18 example.tex
@@
 The subparagraph format with the paragraph indent is likely going to be more familiar to the reader.
+
+\listparagraph[6pt]{Listparagraph}
+{The listparagraph format allows hanging indented lists of options, such as those
+used for class features and background skill/tool proficiency options.}
+
+\listparagraph{Listparagraph}
+{The listparagraph with no vertical space after the previous paragraph.}
 
@@
 
+The text in the first row of the table automatically uses boldface;
+to prevent this, add ``bold=false'' to the optional parameters, for example:
+\begin{lstlisting}[basicstyle=\ttfamily\small]
+[header=Nice Table,bold=false]
+\end{lstlisting}
+
 \subsection{Alternate Table Background}

### 2021-07-11 img/theme-footer.sh
Issue #3. Added helper script to regenerate a version of the footer PDF with a "themed" color instead of the default. The footer generation in dndheader.sty will use the new version if it exists, otherwise will work as it did before. I'd intended to use something like tikz to dynamically draw the footer, but since it's an incomprehensible mystery to me, this workaround will do for now.

@@ -1,0 +1,29 @@
+#!/bin/bash
+
+# A simple shell script to replace the default color in the footerscroll.svg
+# file with an override value, and generate a temporary version of the
+# footer PDF.
+BASEDIR=$(dirname "$0")
+FOOTERFILE=footerscroll.svg
+TEMPFILE=temp${FOOTERFILE}
+
+# Use the first command line parameter as a hex color string (RRGGBB).
+color=$1
+if [ -z "${color}" ]; then
+  echo Color parameter not set, using default \(deca82\)
+  color="deca82"
+fi
+
+# Create temporary copy of the svg file.
+cp -p $BASEDIR/src/${FOOTERFILE} ${BASEDIR}/${TEMPFILE}
+
+# Replace the default color with the option parameter.
+# NOTE: Obviously this will only work if the default color is never changed...
+sed -i 's/deca82/'${color}'/g' ${BASEDIR}/${TEMPFILE}
+
+# Use inkscape to regenerate the footer PDF.
+inkscape -z -A=${BASEDIR}/themed-footerscroll.pdf ${BASEDIR}/${TEMPFILE}
+
+# Clean up
+rm ${BASEDIR}/${TEMPFILE}
+

### 2021-08-12 example.tex
Added a "listparagraph" type that outputs a bolded title with hanging-indent text, used in class features, background options, etc
Reverted default author for consistency with upstream
Expanded the example for the listparagraph format option.

@@
 }
-\author{The rpgTeX Team \and Steve}
+\author{The rpgTeX Team}
 \date{}
@@
 
-\listparagraph[6pt]{Listparagraph}
-{The listparagraph format allows hanging indented lists of options, such as those
-used for class features and background skill/tool proficiency options.}
+\subsubsection{Hanging Indent Features}
+The |listparagraph| format allows hanging indented
+lists of options, such as those used for class features,
+background skill/tool proficiency options, and
+sometimes area features, for example:
 
-\listparagraph{Listparagraph}
-{The listparagraph with no vertical space after the previous paragraph.}
+\listparagraph[6pt]{Doors}
+{The doors are made from thick lumber and are unlocked.}
+
+\listparagraph{Light}
+{The area is illuminated by candles placed in sconces on the
+walls. Each candle has had a \textit{continual flame} spell
+cast on it. Dispelling a flame is rumoured to give grievous offence
+to the host.}
+
+\listparagraph{Ventilation}
+{All areas contain an adequate air supply. The air is renewed
+via lung-like sacks that cling to the ceiling.}
 

### 2021-08-12 article.tex
Added a "listparagraph" type that outputs a bolded title with hanging-indent text, used in class features, background options, etc
Expanded the example for the listparagraph format option.

@@
 The subparagraph format with the paragraph indent is likely going to be more familiar to the reader.
+
+\subsubsection{Hanging Indent Features}
+The |listparagraph| format allows hanging indented
+lists of options, such as those used for class features,
+background skill/tool proficiency options, and
+sometimes area features, for example:
+
+\listparagraph[6pt]{Doors}
+{The doors are made from thick lumber and are unlocked.}
+
+\listparagraph{Light}
+{The area is illuminated by candles placed in sconces on the
+walls. Each candle has had a \textit{continual flame} spell
+cast on it. Dispelling a flame is rumoured to give grievous offence
+to the host.}
+
+\listparagraph{Ventilation}
+{All areas contain an adequate air supply. The air is renewed
+via lung-like sacks that cling to the ceiling.}
 

### 2021-09-05 fancy-example.tex
Ported the hardcover book style from ryumaou, with an optional example (fancy-example.tex) of how to use those features (rather than having a bunch of stuff commented out in example.tex)

--- 2021-08-12 example.tex
@@
-\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode]{dndbook}
+\documentclass[letterpaper,twocolumn,openany,fancy,nodeprecatedcode]{dndbook}
 
@@
 \usepackage{stfloats}
+\usepackage{url}
 \usetikzlibrary{intersections} % Required for ornamentedtabular
@@
 
+% title is not used with the rpgMakeCover and other options below:
 \title{
-  \Huge \scshape \fontfamily{pbk}\selectfont
+  \Huge \scshape \fontfamily{pbk}\fontsize{50}{40}\selectfont
   The Dark \LaTeX{} \\
@@
   \normalfont
-  \large
+  \medskip\Huge
   An Example of the dndbook Class
@@
 \begin{document}
+\rpgMakeCover[
+    image = img/front-cover,
+    logo = img/logo,
+    title = \DndFontTitle\DndTitleContour{RPG Game Book Template},
+    subtitle = \DndFontSubtitle\DndSubtitleContour{An example of the dndbook class,\newline styled like a hardcover book.},
+]
+
+\rpgMakeTitle[
+    title = {RPG Game Book Template},
+    subtitle = {An example of the dndbook class,\newline styled like a hardcover book.},
+    author = {Author McAuthorson},
+    credits = {Copyright © \the\year{} Author McAuthorson\newline\vspace{2ex} Credits:\newline Original fork: \small{\url{https://github.com/rpgtex/DND-5e-LaTeX-Template}}\newline Hardcover style adapted from: \small{\url{https://github.com/ryumaou/RPG-LaTeX-Template-With-Cover}}}
+]
 
 \frontmatter
-
-\maketitle
 
@@
 
+\rpgMakeBackCover[
+    image = img/back-cover,
+    logo = img/logo,
+    title = \DndFontTitle\DndTitleContour{RPG Game Book Template},
+    subtitle = \DndFontSubtitle\DndSubtitleContour{An example of the dndbook class,\newline styled like a hardcover book.},
+    blurbtext = {A blurb or quip to describe the book\\Gather your party!}
+]
+
 \end{document}

### 2021-12-24 article.tex
Added a DndQuote document command, using a similar mechanism to the spell/item header
Added example of changing number of columns in dndlongtable

@@
 On a success, they are no longer charmed.
+
+\subsection{Quotes}
+\DndQuote%
+  {``Sometimes, what you need and what you}
+  {want turn out to be the same thing: An uplifting quote.''}
+  {The Adventurer}
 
@@
     100 & You win a magic item or an expensive piece of classic artwork. \\
+\end{dndlongtable}
+
+Since |dndlongtable| accepts column definitions in the standard |tabular|
+format, alternate numbers of columns can be defined by passing an optional
+parameter. For example, using:
+
+\begin{lstlisting}[basicstyle=\ttfamily\small]
+\begin{dndlongtable}[c p{0.66\linewidth} p{0.1\linewidth}]
+\end{lstlisting}
+
+Yields a three-column table:
+
+\begin{dndlongtable}[c p{0.65\linewidth} p{0.12\linewidth}]
+    \textbf{d100} & \textbf{Result} & \textbf{GP} \\
+    1-2 & You win a magic item or an expensive piece of classic artwork. & 100 gp \\
+    ... & & \\
+    100 & You win a magic item or an expensive piece of classic artwork. & 1000 gp \\
 \end{dndlongtable}

### 2021-12-24 example.tex
Expanded the example for the listparagraph format option.
Tinkering with the title font size
Added a DndQuote document command, using a similar mechanism to the spell/item header
Added example of changing number of columns in dndlongtable

@@
 \title{
-  \Huge \scshape \fontfamily{pbk}\selectfont
+  \Huge \scshape \fontfamily{pbk}\fontsize{50}{40}\selectfont
   The Dark \LaTeX{} \\

### 2022-08-31 article.tex
Added example of setting a numerical proficiency bonus in DndMonster statblock
Added example of single column DndMonster statblock.

@@
 % Monster stat block
+\begin{DndMonster}[float=t]{Monster Foo}
+  \DndMonsterType{Medium aberration (metasyntactic variable), neutral evil}
+
+  % If you want to use commas in the key values, enclose the values in braces.
+  \DndMonsterBasics[
+      armor-class = {9 (12 with \emph{mage armor})},
+      hit-points  = {\DndDice{3d8 + 3}},
+      speed       = {30 ft., fly 30 ft.},
+    ]
+
+  \DndMonsterAbilityScores[
+      str = 12,
+      dex = 8,
+      con = 13,
+      int = 10,
+      wis = 14,
+      cha = 15,
+    ]
+
+  \DndMonsterDetails[
+      %saving-throws = {Str +0, Dex +0, Con +0, Int +0, Wis +0, Cha +0},
+      %skills = {Acrobatics +0, Animal Handling +0, Arcana +0, Athletics +0, Deception +0, History +0, Insight +0, Intimidation +0, Investigation +0, Medicine +0, Nature +0, Perception +0, Performance +0, Persuasion +0, Religion +0, Sleight of Hand +0, Stealth +0, Survival +0},
+      %damage-vulnerabilities = {cold},
+      %damage-resistances = {bludgeoning, piercing, and slashing from nonmagical attacks},
+      %damage-immunities = {poison},
+      %condition-immunities = {poisoned},
+      senses = {darkvision 60 ft., passive Perception 10},
+      languages = {Common, Goblin, Undercommon},
+      challenge = ---,
+      proficiency = equals your bonus
+    ]
+  % Traits
+  \DndMonsterAction{Innate Spellcasting}
+  Foo's spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It can innately cast the following spells, requiring no material components:
+  \begin{DndMonsterSpells}
+    \DndInnateSpellLevel{misty step}
+    \DndInnateSpellLevel[3]{fog cloud, rope trick}
+    \DndInnateSpellLevel[1]{identify}
+  \end{DndMonsterSpells}
+
+  \DndMonsterAction{Spellcasting}
+  Foo is a 2nd-level spellcaster. Its spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It has the following sorcerer spells prepared:
+  \begin{DndMonsterSpells}
+    \DndMonsterSpellLevel{blade ward, fire bolt, light, shocking grasp}
+    \DndMonsterSpellLevel[1][3]{burning hands, mage armor, shield}
+  \end{DndMonsterSpells}
+
+  \DndMonsterSection{Actions}
+  \DndMonsterAction{Multiattack}
+  The foo makes two melee attacks.
+
+  %Default values are shown commented out
+  \DndMonsterAttack[
+    name=Dagger,
+    %distance=both, % valid options are in the set {both,melee,ranged},
+    %type=weapon, %valid options are in the set {weapon,spell}
+    mod=+3,
+    %reach=5,
+    %range=20/60,
+    %targets=one target,
+    dmg=\DndDice{1d4+1},
+    dmg-type=piercing,
+    %plus-dmg=,
+    %plus-dmg-type=,
+    %or-dmg=,
+    %or-dmg-when=,
+    %extra=,
+  ]
+
+  %\DndMonsterMelee calls \DndMonsterAttack with the melee option
+  \DndMonsterMelee[
+    name=Flame Tongue Longsword,
+    mod=+3,
+    %reach=5,
+    %targets=one target,
+    dmg=\DndDice{1d8+1},
+    dmg-type=slashing,
+    plus-dmg=\DndDice{2d6},
+    plus-dmg-type=fire,
+    or-dmg=\DndDice{1d10+1},
+    or-dmg-when=if used with two hands,
+    %extra=,
+  ]
+
+  %\DndMonsterRanged calls \DndMonsterAttack with the ranged option
+  \DndMonsterRanged[
+    name=Assassin's Light Crossbow,
+    mod=+1,
+    range=80/320,
+    dmg=\DndDice{1d8},
+    dmg-type=piercing,
+    %plus-dmg=,
+    %plus-dmg-type=,
+    %or-dmg=,
+    %or-dmg-when=,
+    extra={, and the target must make a DC 15 Constitution saving throw, taking 24 (7d6) poison damage on a failed save, or half as much damage on a successful one}
+  ]
+
+  % Legendary Actions
+  \DndMonsterSection{Legendary Actions}
+  The foo can take 3 legendary actions, choosing from the options below.
+Only one legendary action option can be used at a time and only at the end of another creature's turn.
+The foo regains spent legendary actions at the start of its turn.
+
+  \begin{DndMonsterLegendaryActions}
+    \DndMonsterLegendaryAction{Move}{The foo moves up to its speed.}
+    \DndMonsterLegendaryAction{Dagger Attack}{The foo makes a dagger attack.}
+    \DndMonsterLegendaryAction{Create Contract (Costs 3 Actions)}{The foo presents a contract in a language it knows and waves it in the face of a creature within 10 feet.
+The creature must make a DC 10 Intelligence saving throw.
+On a failure, the creature is incapacitated until the start of the foo's next turn.
+A creature who cannot read the language in which the contract is written has advantage on this saving throw.}
+  \end{DndMonsterLegendaryActions}
+\end{DndMonster}
+
+% Monster stat block
 \begin{DndMonster}[float*=b,width=\textwidth + 8pt]{Monster Foo}
@@
         challenge = 1,
+        proficiency = +2,
       ]

### 2022-08-31 article.tex
Added note on single column DndMonster.
Bit of layout for the monster tables; still bad, needs work

@@
 
+\clearpage
+
 \section{Monsters and NPCs}
+The |DndMonster| environment is used to typeset monster and NPC stat blocks. The module supplies many functions to easily typeset the contents of the stat block.
+
+The stat block can be formatted either as a single column, or as a block that spans the page horizontally.
 
 % Monster stat block
-\begin{DndMonster}[float=t]{Monster Foo}
+\begin{DndMonster}[float=h]{Monster Foo}
   \DndMonsterType{Medium aberration (metasyntactic variable), neutral evil}
@@
 
-The |DndMonster| environment is used to typeset monster and NPC stat blocks. The module supplies many functions to easily typeset the contents of the stat block
+\clearpage
 

### 2022-10-16 example.tex
Added example of changing number of columns in dndlongtable
Added example of setting a numerical proficiency bonus in DndMonster statblock
Fixed table colour for tables from Basic Rules

@@
         challenge = 1,
-        %proficiency = +2,
+        proficiency = +2,
       ]
@@
     \rowcolor{BrGreen}
-    |BrGreen|                       & Gray-green used for tables in Basic Rules\\
+    |BrGreen|                       & Light-gray used for tables in Basic Rules\\
   \end{tabularx}

### 2022-10-27 article.tex
Fixed table colour for tables from Basic Rules
Added example showing how to split a table across the column.

@@
 \end{DndAltTable}
+
+\subsection{Split Tables}
+Temporarily adding a column using |multicols| can
+be used to achieve the effect of a split column
+table.
+
+Add the following around two or more tables (note
+the non-breaking space character (\char`\~) used for
+the table header on all but the first):
+
+\begin{lstlisting}[basicstyle=\ttfamily\small]
+\begin{multicols}{2}
+\begin{DndAltTable}[header=Encounters]{cX}
+...
+\end{DndAltTable}
+\begin{DndAltTable}[header=~]{cX}
+...
+\end{DndAltTable}
+\end{multicols}
+\end{lstlisting}
+
+This achieves the following effect:
+
+\begin{multicols}{2}
+\begin{DndAltTable}[header=Encounters]{cX}
+    \textbf{d10} & \textbf{Encounter} \\
+    1  & Toppled statue \\
+    2  & Ferocious kitten \\
+    3  & Broken sign \\
+    4  & Blind beggar \\
+    5  & Piercing wail \\
+\end{DndAltTable}
+\begin{DndAltTable}[header=~]{cX}
+    \textbf{d10} & \textbf{Encounter} \\
+    6  & Pack of wolves \\
+    7  & Drunk owlbear \\
+    8  & Freed prisoners \\
+    9  & Wild magic zone \\
+    10 & Magic item \\
+\end{DndAltTable}
+\end{multicols}
 
@@
     \rowcolor{BrGreen}
-    |BrGreen|                       & Gray-green used for tables in Basic Rules\\
+    |BrGreen|                       & Light-gray used for tables in Basic Rules\\
   \end{DndTable}

### 2022-12-21 article.tex
Fixed typo in "\listparagraph" example

@@
 \subsubsection{Hanging Indent Features}
-The |listparagraph| format allows hanging indented
+The |\listparagraph| format allows hanging indented
 lists of options, such as those used for class features,

### 2024-09-27 example.tex
Added spanning title in multi-column table example
New "stats=modern" option to enable modern (MM2024) stat block appearance.

--- 2022-10-16 example.tex
@@
-\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode]{dndbook}
+\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode,stats=modern]{dndbook}
 
@@
 
-\title{
-  \Huge \scshape \fontfamily{pbk}\fontsize{50}{40}\selectfont
-  The Dark \LaTeX{} \\
-  \medskip
-  \normalfont
-  \medskip\Huge
-  An Example of the dndbook Class
-}
+\title{The Dark \LaTeX{} \\
+\large An Example of the dndbook Class}
 \author{The rpgTeX Team}
-\date{}
+\date{2020/04/21}
 
@@
 
-\subsubsection{Hanging Indent Features}
-The |listparagraph| format allows hanging indented
-lists of options, such as those used for class features,
-background skill/tool proficiency options, and
-sometimes area features, for example:
-
-\listparagraph[6pt]{Doors}
-{The doors are made from thick lumber and are unlocked.}
-
-\listparagraph{Light}
-{The area is illuminated by candles placed in sconces on the
-walls. Each candle has had a \textit{continual flame} spell
-cast on it. Dispelling a flame is rumoured to give grievous offence
-to the host.}
-
-\listparagraph{Ventilation}
-{All areas contain an adequate air supply. The air is renewed
-via lung-like sacks that cling to the ceiling.}
-
 \section{Special Sections}
@@
 
-\subsection{Quotes}
-\DndQuote%
-  {``Sometimes, what you need and what you}
-  {want turn out to be the same thing: An uplifting quote.''}
-  {The Adventurer}
-
 \section{Map Regions}
 The map region functions |\DndArea| and |\DndSubArea| provide automatic numbering of areas.
-
-The command |\DndMap{title}| creates a new map index (A, B, C\ldots).
-This doesn't add anything to the document, but the map index can be referenced with |\ref{map:title}|.
-For example, the Kingdom is map\,\ref{map:The Kingdom}.
-
-\DndMap{The Kingdom}
-
-Areas can be references with |\ref{area:name}|. For example, Mount Doofus is area \ref{area:Mount Doofus}.
 
@@
 
-\section{Alternate Map Region Styles}
-Published modules sometimes use plain numbers for locations, sometimes plain
-letters, and sometimes they prefix a character to the front of the numbers.
-The following options can be used to display in these forms:
-
-\numberedarea{Numbered Dungeon}
-Areas in the Numbered Dungeon have sequential numbers. This is done using
-the following commands:
-
-\begin{verbatim}
-\numberedarea{Numbered Dungeon}
-\numberedsubarea{Entry}
-\numberedsubarea{Trap}
-\numberedsubarea{Fight}
-\numberedsubarea{Exit}
-\end{verbatim}
-
-These commands yield the following results:
-\numberedsubarea{Entry}
-\numberedsubarea{Trap}
-\numberedsubarea{Fight}
-\numberedsubarea{Exit}
-
-\letteredarea{Lettered Dungeon}
-Areas in the Lettered Dungeon are labelled with sequential characters
-(A, B, C, etc). This is done using the following commands:
-
-\begin{verbatim}
-\letteredarea{Lettered Dungeon}
-\letteredsubarea{Entry}
-\letteredsubarea{Trap}
-\letteredsubarea{Fight}
-\letteredsubarea{Exit}
-\end{verbatim}
-
-These commands yield the following results:
-\letteredsubarea{Entry}
-\letteredsubarea{Trap}
-\letteredsubarea{Fight}
-\letteredsubarea{Exit}
-
-\prefixedarea{Prefixed Dungeon}{Z}
-Areas in the Prefixed Dungeon have a custom prefix character,
-in this case: `\prefixedareaprefix'.
-This is done using the following commands:
-
-\begin{verbatim}
-\prefixedarea{Prefixed Dungeon}{Z}
-\prefixedsubarea{Entry}
-\prefixedsubarea{Trap}
-\prefixedsubarea{Fight}
-\prefixedsubarea{Exit}
-\end{verbatim}
-
-These commands yield the following results:
-\prefixedsubarea{Entry}
-\prefixedsubarea{Trap}
-\prefixedsubarea{Fight}
-\prefixedsubarea{Exit}
-
-\section{Map References}
-
-\DndArea[The Kingdom]{Mount Doofus}
-This area has a map reference before the number. The map name is an optional parameter on |\DndArea|. Useful if your document contains multiple maps!
-
 \chapter{Text Boxes}
 
-The module has three environments for setting text apart so that it is drawn to the reader's attention. |DndReadAloud| is used for text that a game master would read aloud.
+The module has several environments for setting text apart so that it is drawn to the reader's attention. |DndReadAloud| is used for text that a game master would read aloud.
 
@@
 \section{As an Aside}
-The other two environments are the |DndComment| and the |DndSidebar|. The |DndComment| is breakable and can safely be used inline in the text.
+The next two environments are the |DndComment| and the |DndSidebar|. The |DndComment| is breakable and can safely be used inline in the text.
 
@@
 \begin{DndSidebar}[float=!b]{Behold the DndSidebar!}
-\tocside{Behold the DndSidebar!}
   The |DndSidebar| is used as a sidebar.
 It does not break over columns and is best used with a figure environment to float it to one corner of the page where the surrounding text can then flow around it.
-
-  Use the |\tocside{title}| command to create an entry in the table of contents, if you want.
 \end{DndSidebar}
 
+You can represent an attached note (for example, for notes from Bigby or Mordenkainen) using the |DndAside| environment.
+
+\begin{DndAside}
+  This is the part where I give you a little extra information or make a witty comment to keep you entertained while you read.
+\end{DndAside}
+
+\begin{DndQuotation}{The Author}
+  This is the part where I give you a little extra information or make a witty comment to keep you entertained while you read.
+\end{DndQuotation}
+
 \section{Tables}
-
-\subsection{Regular Table}
 The |DndTable| colors the even rows and is set to the width of a line by default.
@@
 
-The text in the first row of the table automatically uses boldface;
-to prevent this, add ``bold=false'' to the optional parameters, for example:
-\begin{lstlisting}[basicstyle=\ttfamily\small]
-[header=Nice Table,bold=false]
-\end{lstlisting}
-
-\subsection{Alternate Table Background}
-
-The |DndAltTable| allows tables that have a blank "header" line followed
-by alternating theme color and white background, as per some of the sourcebooks.
-
-\begin{DndAltTable}[header=Alternate Table,bold=false]{cX}
-    \textbf{Table head} & \textbf{Table head} \\
-    Some value  & Some value \\
-    Some value  & Some value \\
-    Some value  & Some value \\
-    Some value  & Some value \\
-\end{DndAltTable}
-
-\subsection{Long Table that Spans Pages}
-
-The |dndlongtable| allows table that can span multiple pages. The current
-version is configured to do a two-column table.
-
-\begin{dndlongtable}
-    \textbf{Roll (d100)} & \textbf{Result} \\
-    1-2 & You win a magic item or an expensive piece of classic artwork. \\
-    3-4 & You win a magic item or an expensive piece of classic artwork. \\
-    5-6 & You win a magic item or an expensive piece of classic artwork. \\
-    7-8 & You win a magic item or an expensive piece of classic artwork. \\
-    9-10 & You win a magic item or an expensive piece of classic artwork. \\
-    11-12 & You win a magic item or an expensive piece of classic artwork. \\
-    13-14 & You win a magic item or an expensive piece of classic artwork. \\
-    15-16 & You win a magic item or an expensive piece of classic artwork. \\
-    17-18 & You win a magic item or an expensive piece of classic artwork. \\
-    19-20 & You win a magic item or an expensive piece of classic artwork. \\
-    20-22 & You win a magic item or an expensive piece of classic artwork. \\
-    23-24 & You win a magic item or an expensive piece of classic artwork. \\
-    25-26 & You win a magic item or an expensive piece of classic artwork. \\
-    27-28 & You win a magic item or an expensive piece of classic artwork. \\
-    29-30 & You win a magic item or an expensive piece of classic artwork. \\
-    31-32 & You win a magic item or an expensive piece of classic artwork. \\
-    33-34 & You win a magic item or an expensive piece of classic artwork. \\
-    35-36 & You win a magic item or an expensive piece of classic artwork. \\
-    37-38 & You win a magic item or an expensive piece of classic artwork. \\
-    39-40 & You win a magic item or an expensive piece of classic artwork. \\
-    41-42 & You win a magic item or an expensive piece of classic artwork. \\
-    43-44 & You win a magic item or an expensive piece of classic artwork. \\
-    45-46 & You win a magic item or an expensive piece of classic artwork. \\
-    47-48 & You win a magic item or an expensive piece of classic artwork. \\
-    49-50 & You win a magic item or an expensive piece of classic artwork. \\
-    51-52 & You win a magic item or an expensive piece of classic artwork. \\
-    53-54 & You win a magic item or an expensive piece of classic artwork. \\
-    55-56 & You win a magic item or an expensive piece of classic artwork. \\
-    57-58 & You win a magic item or an expensive piece of classic artwork. \\
-    59-60 & You win a magic item or an expensive piece of classic artwork. \\
-    61-62 & You win a magic item or an expensive piece of classic artwork. \\
-    63-64 & You win a magic item or an expensive piece of classic artwork. \\
-    65-66 & You win a magic item or an expensive piece of classic artwork. \\
-    67-68 & You win a magic item or an expensive piece of classic artwork. \\
-    69-70 & You win a magic item or an expensive piece of classic artwork. \\
-    71-72 & You win a magic item or an expensive piece of classic artwork. \\
-    73-74 & You win a magic item or an expensive piece of classic artwork. \\
-    75-76 & You win a magic item or an expensive piece of classic artwork. \\
-    77-78 & You win a magic item or an expensive piece of classic artwork. \\
-    79-80 & You win a magic item or an expensive piece of classic artwork. \\
-    81 & You win a magic item or an expensive piece of classic artwork. \\
-    82 & You win a magic item or an expensive piece of classic artwork. \\
-    83 & You win a magic item or an expensive piece of classic artwork. \\
-    84 & You win a magic item or an expensive piece of classic artwork. \\
-    85 & You win a magic item or an expensive piece of classic artwork. \\
-    86 & You win a magic item or an expensive piece of classic artwork. \\
-    87 & You win a magic item or an expensive piece of classic artwork. \\
-    88 & You win a magic item or an expensive piece of classic artwork. \\
-    89 & You win a magic item or an expensive piece of classic artwork. \\
-    90 & You win a magic item or an expensive piece of classic artwork. \\
-    91 & You win a magic item or an expensive piece of classic artwork. \\
-    92 & You win a magic item or an expensive piece of classic artwork. \\
-    93 & You win a magic item or an expensive piece of classic artwork. \\
-    94 & You win a magic item or an expensive piece of classic artwork. \\
-    95 & You win a magic item or an expensive piece of classic artwork. \\
-    96 & You win a magic item or an expensive piece of classic artwork. \\
-    97 & You win a magic item or an expensive piece of classic artwork. \\
-    98 & You win a magic item or an expensive piece of classic artwork. \\
-    99 & You win a magic item or an expensive piece of classic artwork. \\
-    100 & You win a magic item or an expensive piece of classic artwork. \\
-\end{dndlongtable}
-
-Since |dndlongtable| accepts column definitions in the standard |tabular|
-format, alternate numbers of columns can be defined by passing an optional
-parameter. For example, using:
-
-\begin{lstlisting}[basicstyle=\ttfamily\small]
-\begin{dndlongtable}[c p{0.66\linewidth} p{0.1\linewidth}]
-\end{lstlisting}
-
-Yields a three-column table:
-
-\begin{dndlongtable}[c p{0.65\linewidth} p{0.12\linewidth}]
-    \textbf{d100} & \textbf{Result} & \textbf{GP} \\
-    1-2 & You win a magic item or an expensive piece of classic artwork. & 100 gp \\
-    ... & & \\
-    100 & You win a magic item or an expensive piece of classic artwork. & 1000 gp \\
-\end{dndlongtable}
-
-\subsection{Tables with Footnotes}
-Surrounding one of the existing table types with a |minipage| section
-allows footnotes declared in the table to appear at the end of the table,
-rather than in the page footer as normal. For a regularly sized table
-in the two-column layout, the following declaration can be used:
-
-\begin{lstlisting}[basicstyle=\ttfamily\small]
-\begin{minipage}{8cm}
-  \begin{DndTable}
-    ...
-    ...
-  \end{DndTable}
-\end{minipage}
-\end{lstlisting}
-
-To achieve the following effect:
-
-\begin{minipage}{8cm}
-  \begin{DndTable}[header=Footnoted Table]{lX}
-    \textbf{Table head\footnote{\enspace Something to note}} & \textbf{Table head} \\
-    Some value  & Some value\footnote{\enspace Another thing to note} \\
-    Some value  & Some value \\
-    Some value  & Some value \\
-    Some value\footnote{\enspace The most important note}  & Some value \\
-  \end{DndTable}
-\end{minipage}
-
-\subsection{Ornamented Tables}
-The |ornamentedtabular| allows tables similar to those used for spellcasters
-(see over page).
-
-\begin{figure*}[h!]
-\begin{ornamentedtabular}{ccp{3.0cm}ccccccccccc}[title={The Full Caster}]
-  & & & & & \multicolumn{9}{c}{\thead{--- Spell Slots per Spell Level ---}} \\
-  \textbf{Level} & \textbf{\makecell{Proficiency\\Bonus}} & \textbf{Features} & \textbf{\makecell{Cantrips\\Known}} & \textbf{\makecell{Spells\\Known}} & \textbf{1st} & \textbf{2nd} & \textbf{3rd} & \textbf{4th} & \textbf{5th} & \textbf{6th} & \textbf{7th} & \textbf{8th} & \textbf{9th} \\
-  1st  & +2 & Feature & 3 & 4  & 2 & — & — & — & — & — & — & — & — \\
-  2nd  & +2 & Feature & 3 & 4  & 3 & — & — & — & — & — & — & — & — \\
-  3rd  & +2 & Feature & 3 & 4  & 4 & 2 & — & — & — & — & — & — & — \\
-  4th  & +2 & Feature & 4 & 5  & 4 & 3 & — & — & — & — & — & — & — \\
-  5th  & +3 & Feature & 4 & 6  & 4 & 3 & 2 & — & — & — & — & — & — \\
-  6th  & +3 & Feature & 4 & 7  & 4 & 3 & 3 & — & — & — & — & — & — \\
-  7th  & +3 & Feature & 4 & 8  & 4 & 3 & 3 & 1 & — & — & — & — & — \\
-  8th  & +3 & Feature & 4 & 9  & 4 & 3 & 3 & 2 & — & — & — & — & — \\
-  9th  & +4 & Feature & 4 & 10 & 4 & 3 & 3 & 3 & 1 & — & — & — & — \\
-  10th & +4 & Feature & 5 & 11 & 4 & 3 & 3 & 3 & 2 & — & — & — & — \\
-  11th & +4 & Feature & 5 & 12 & 4 & 3 & 3 & 3 & 2 & 1 & — & — & — \\
-  12th & +4 & Feature & 5 & 12 & 4 & 3 & 3 & 3 & 2 & 1 & — & — & — \\
-  13th & +5 & Feature & 5 & 13 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & — & — \\
-  14th & +5 & Feature & 5 & 13 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & — & — \\
-  15th & +5 & Feature & 5 & 14 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & — \\
-  16th & +5 & Feature & 5 & 14 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & — \\
-  17th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & 1 \\
-  18th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 1 & 1 & 1 & 1 \\
-  19th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 2 & 1 & 1 & 1 \\
-  20th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 2 & 2 & 1 & 1 \\
-\end{ornamentedtabular}
-\end{figure*}
-
 \chapter{Monsters and NPCs}
-
-% Monster stat block
-\begin{DndMonster}[float=t]{Monster Foo}
-  \DndMonsterType{Medium aberration (metasyntactic variable), neutral evil}
-
-  % If you want to use commas in the key values, enclose the values in braces.
-  \DndMonsterBasics[
-      armor-class = {9 (12 with \emph{mage armor})},
-      hit-points  = {\DndDice{3d8 + 3}},
-      speed       = {30 ft., fly 30 ft.},
-    ]
-
-  \DndMonsterAbilityScores[
-      str = 12,
-      dex = 8,
-      con = 13,
-      int = 10,
-      wis = 14,
-      cha = 15,
-    ]
-
-  \DndMonsterDetails[
-      %saving-throws = {Str +0, Dex +0, Con +0, Int +0, Wis +0, Cha +0},
-      %skills = {Acrobatics +0, Animal Handling +0, Arcana +0, Athletics +0, Deception +0, History +0, Insight +0, Intimidation +0, Investigation +0, Medicine +0, Nature +0, Perception +0, Performance +0, Persuasion +0, Religion +0, Sleight of Hand +0, Stealth +0, Survival +0},
-      %damage-vulnerabilities = {cold},
-      %damage-resistances = {bludgeoning, piercing, and slashing from nonmagical attacks},
-      %damage-immunities = {poison},
-      %condition-immunities = {poisoned},
-      senses = {darkvision 60 ft., passive Perception 10},
-      languages = {Common, Goblin, Undercommon},
-      challenge = ---,
-      proficiency = equals your bonus
-    ]
-  % Traits
-  \DndMonsterAction{Innate Spellcasting}
-  Foo's spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It can innately cast the following spells, requiring no material components:
-  \begin{DndMonsterSpells}
-    \DndInnateSpellLevel{misty step}
-    \DndInnateSpellLevel[3]{fog cloud, rope trick}
-    \DndInnateSpellLevel[1]{identify}
-  \end{DndMonsterSpells}
-
-  \DndMonsterAction{Spellcasting}
-  Foo is a 2nd-level spellcaster. Its spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It has the following sorcerer spells prepared:
-  \begin{DndMonsterSpells}
-    \DndMonsterSpellLevel{blade ward, fire bolt, light, shocking grasp}
-    \DndMonsterSpellLevel[1][3]{burning hands, mage armor, shield}
-  \end{DndMonsterSpells}
-
-  \DndMonsterSection{Actions}
-  \DndMonsterAction{Multiattack}
-  The foo makes two melee attacks.
-
-  %Default values are shown commented out
-  \DndMonsterAttack[
-    name=Dagger,
-    %distance=both, % valid options are in the set {both,melee,ranged},
-    %type=weapon, %valid options are in the set {weapon,spell}
-    mod=+3,
-    %reach=5,
-    %range=20/60,
-    %targets=one target,
-    dmg=\DndDice{1d4+1},
-    dmg-type=piercing,
-    %plus-dmg=,
-    %plus-dmg-type=,
-    %or-dmg=,
-    %or-dmg-when=,
-    %extra=,
-  ]
-
-  %\DndMonsterMelee calls \DndMonsterAttack with the melee option
-  \DndMonsterMelee[
-    name=Flame Tongue Longsword,
-    mod=+3,
-    %reach=5,
-    %targets=one target,
-    dmg=\DndDice{1d8+1},
-    dmg-type=slashing,
-    plus-dmg=\DndDice{2d6},
-    plus-dmg-type=fire,
-    or-dmg=\DndDice{1d10+1},
-    or-dmg-when=if used with two hands,
-    %extra=,
-  ]
-
-  %\DndMonsterRanged calls \DndMonsterAttack with the ranged option
-  \DndMonsterRanged[
-    name=Assassin's Light Crossbow,
-    mod=+1,
-    range=80/320,
-    dmg=\DndDice{1d8},
-    dmg-type=piercing,
-    %plus-dmg=,
-    %plus-dmg-type=,
-    %or-dmg=,
-    %or-dmg-when=,
-    extra={, and the target must make a DC 15 Constitution saving throw, taking 24 (7d6) poison damage on a failed save, or half as much damage on a successful one}
-  ]
-
-  % Legendary Actions
-  \DndMonsterSection{Legendary Actions}
-  The foo can take 3 legendary actions, choosing from the options below.
-Only one legendary action option can be used at a time and only at the end of another creature's turn.
-The foo regains spent legendary actions at the start of its turn.
-
-  \begin{DndMonsterLegendaryActions}
-    \DndMonsterLegendaryAction{Move}{The foo moves up to its speed.}
-    \DndMonsterLegendaryAction{Dagger Attack}{The foo makes a dagger attack.}
-    \DndMonsterLegendaryAction{Create Contract (Costs 3 Actions)}{The foo presents a contract in a language it knows and waves it in the face of a creature within 10 feet.
-The creature must make a DC 10 Intelligence saving throw.
-On a failure, the creature is incapacitated until the start of the foo's next turn.
-A creature who cannot read the language in which the contract is written has advantage on this saving throw.}
-  \end{DndMonsterLegendaryActions}
-\end{DndMonster}
 
@@
         speed       = {30 ft., fly 30 ft.},
+        initiative  = --1,
       ]
@@
         challenge = 1,
-        proficiency = +2,
       ]
-    % Traits
+
+    \DndMonsterSection{Traits}
     \DndMonsterAction{Innate Spellcasting}
@@
     \rowcolor{DmgSlateGray}
-    |DmgSlateGray| (|DmgSlateGrey|) & Blue-gray used in DMG Part 3 \\
+    |DmgSlateGray| (|DmgSlateGrey|) & Blue-gray used in PHB Part 3 \\
     \rowcolor{DmgLilac}
@@
     \rowcolor{BrGreen}
-    |BrGreen|                       & Light-gray used for tables in Basic Rules\\
+    |BrGreen|                       & Gray-green used for tables in Basic Rules\\
   \end{tabularx}
@@
 
-\subsection{Extra Theme Color Control}
-Use |\DndSetComplexThemeColor| in order to have more precise control over the various theme colors defined within the document class.
-This command takes eight (8) |<color>| values that map to the following color variables within the theme:
-
-\begin{DndTable}[header=Complex Theme Parameter Map]{clX}
-  \textbf{\#} & \textbf{Variable Set} & \textbf{Affected Style} \\
-  1 & \textit{themecolor} & Used in |DndSetThemeColor|; set for future compatibility \\
-    & \textit{tablecolor} & |DndTable| \\
-  2 & \textit{commentcolor} & |DndComment| \\
-  3 & \textit{sidebarcolor} & |DndSidebar| \\
-  4 & \textit{readaloudcolor} & |DndReadAloud| background \\
-  5 & \textit{readaloudbordercolor} & |DndReadAloud| border \\
-  6 & \textit{titlecolor} & Titles of sections (|section|, |subsection|, etc) \\
-  7 & \textit{titlerulecolor} & |subsection| title ruling \\
-  8 & \textit{pagecolor} & Page numbers and footer \\
-\end{DndTable}
-
-\begin{DndComment}{Note On Changing Schemes}
-If a major color scheme change is attempted, it is
-likely that the background ``paper'' (which can be overridden with
-|\SetPaperImage|) and |footerscroll.pdf| will need
-to be modified as well in order to fit the other color modifications.
-\end{DndComment}
-
-An example of these settings for a theme similar to the \textit{Ghosts of Saltmarsh} sourcebook.
-Note that the values for \textit{titlered} and \textit{titlegold} are used for the title and title rule colours unchanged in this example.
-
-\begin{lstlisting}[basicstyle=\ttfamily\small]
-\definecolor {mytheme} {HTML} {DCF1E5}
-\definecolor {mycomment} {HTML} {E9F5F5}
-\definecolor {mysidebar} {HTML} {E9F5F5}
-\definecolor {myreadaloud} {HTML} {DCF1E5}
-\definecolor {myreadaloudborder} {HTML} {8AA7A2}
-\definecolor {mypagenum} {HTML} {B5D4CF}
-\DndSetComplexThemeColor[mytheme][mycomment][mysidebar][myreadaloud][myreadaloudborder][titlered][titlegold][mypagenum]
-\end{lstlisting}
-
-\part{Appendices}
-
-\appendix
-
-\chapter{One Last Thing}
-
-\DndDropCapLine{U}sing the |\appendix| command causes all subsequent chapters to be formatted as appendices. Neat!
-
 \end{document}

### 2024-09-30 example.tex
Adjustments for modern stats basic block layout. Fixed quotation/aside font selection in default font set.
Some updates to the example document; notes on aside & quotation environments, examples & info on modern stat blocks.

@@
-\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode,stats=modern]{dndbook}
+\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode]{dndbook}
 
@@
 \usepackage{stfloats}
+\usepackage{wrapfig}
 
@@
 
+The |DndQuotation| environment goes a little further, offering the option of comment attribution, and tilts the note at a slight angle.
+
 \begin{DndQuotation}{The Author}
@@
 \chapter{Monsters and NPCs}
+
+% Monster stat block
+\begin{DndMonster}[float*=b,width=\textwidth + 8pt]{Monster Foo}
+  \begin{multicols}{2}
+    \DndMonsterType{Medium aberration (metasyntactic variable), neutral evil}
+
+    % If you want to use commas in the key values, enclose the values in braces.
+    \DndMonsterBasics[
+        armor-class = {9 (12 with \emph{mage armor})},
+        hit-points  = {\DndDice{3d8 + 3}},
+        speed       = {30 ft., fly 30 ft.},
+      ]
+
+    \DndMonsterAbilityScores[
+        str = 12,
+        dex = 8,
+        con = 13,
+        int = 10,
+        wis = 14,
+        cha = 15,
+      ]
+
+    \DndMonsterDetails[
+        %saving-throws = {Str +0, Dex +0, Con +0, Int +0, Wis +0, Cha +0},
+        %skills = {Acrobatics +0, Animal Handling +0, Arcana +0, Athletics +0, Deception +0, History +0, Insight +0, Intimidation +0, Investigation +0, Medicine +0, Nature +0, Perception +0, Performance +0, Persuasion +0, Religion +0, Sleight of Hand +0, Stealth +0, Survival +0},
+        %damage-vulnerabilities = {cold},
+        %damage-resistances = {bludgeoning, piercing, and slashing from nonmagical attacks},
+        %damage-immunities = {poison},
+        %condition-immunities = {poisoned},
+        senses = {darkvision 60 ft., passive Perception 10},
+        languages = {Common, Goblin, Undercommon},
+        challenge = 1,
+      ]
+
+    \DndMonsterAction{Innate Spellcasting}
+    Foo's spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It can innately cast the following spells, requiring no material components:
+    \begin{DndMonsterSpells}
+      \DndInnateSpellLevel{misty step}
+      \DndInnateSpellLevel[3]{fog cloud, rope trick}
+      \DndInnateSpellLevel[1]{identify}
+    \end{DndMonsterSpells}
+
+    \DndMonsterAction{Spellcasting}
+    Foo is a 2nd-level spellcaster. Its spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It has the following sorcerer spells prepared:
+    \begin{DndMonsterSpells}
+      \DndMonsterSpellLevel{blade ward, fire bolt, light, shocking grasp}
+      \DndMonsterSpellLevel[1][3]{burning hands, mage armor, shield}
+    \end{DndMonsterSpells}
+
+    \DndMonsterSection{Actions}
+    \DndMonsterAction{Multiattack}
+    The foo makes two melee attacks.
+
+    %Default values are shown commented out
+    \DndMonsterAttack[
+      name=Dagger,
+      %distance=both, % valid options are in the set {both,melee,ranged},
+      %type=weapon, %valid options are in the set {weapon,spell}
+      mod=+3,
+      %reach=5,
+      %range=20/60,
+      %targets=one target,
+      dmg=\DndDice{1d4+1},
+      dmg-type=piercing,
+      %plus-dmg=,
+      %plus-dmg-type=,
+      %or-dmg=,
+      %or-dmg-when=,
+      %extra=,
+    ]
+
+    %\DndMonsterMelee calls \DndMonsterAttack with the melee option
+    \DndMonsterMelee[
+      name=Flame Tongue Longsword,
+      mod=+3,
+      %reach=5,
+      %targets=one target,
+      dmg=\DndDice{1d8+1},
+      dmg-type=slashing,
+      plus-dmg=\DndDice{2d6},
+      plus-dmg-type=fire,
+      or-dmg=\DndDice{1d10+1},
+      or-dmg-when=if used with two hands,
+      %extra=,
+    ]
+
+    %\DndMonsterRanged calls \DndMonsterAttack with the ranged option
+    \DndMonsterRanged[
+      name=Assassin's Light Crossbow,
+      mod=+1,
+      range=80/320,
+      dmg=\DndDice{1d8},
+      dmg-type=piercing,
+      %plus-dmg=,
+      %plus-dmg-type=,
+      %or-dmg=,
+      %or-dmg-when=,
+      extra={, and the target must make a DC 15 Constitution saving throw, taking 24 (7d6) poison damage on a failed save, or half as much damage on a successful one}
+    ]
+
+    % Legendary Actions
+    \DndMonsterSection{Legendary Actions}
+    The foo can take 3 legendary actions, choosing from the options below.
+Only one legendary action option can be used at a time and only at the end of another creature's turn.
+The foo regains spent legendary actions at the start of its turn.
+
+    \begin{DndMonsterLegendaryActions}
+      \DndMonsterLegendaryAction{Move}{The foo moves up to its speed.}
+      \DndMonsterLegendaryAction{Dagger Attack}{The foo makes a dagger attack.}
+      \DndMonsterLegendaryAction{Create Contract (Costs 3 Actions)}{The foo presents a contract in a language it knows and waves it in the face of a creature within 10 feet.
+The creature must make a DC 10 Intelligence saving throw.
+On a failure, the creature is incapacitated until the start of the foo's next turn.
+A creature who cannot read the language in which the contract is written has advantage on this saving throw.}
+    \end{DndMonsterLegendaryActions}
+  \end{multicols}
+\end{DndMonster}
+
+The |DndMonster| environment is used to typeset monster and NPC stat blocks. The module supplies many functions to easily typeset the contents of the stat block.
+
+When used with the |stats=modern| package option, some additional values are available for customization: |DndMonsterBasics| takes an |initiative| option to display as part of the initial block; it appears to the right of the \textbf{Armor Class} option.
+The |DndMonsterAbilityScores| command now has options for |str save|, |dex save|, etc, which if provided will replace the values in the appropriate \textbf{save} column of the abilities block.
+Lastly, modern stat blocks use an explicit section title for traits (the actions appearing between |DndMonsterDetails| and the \textbf{Actions} section).
+WotC also seems to have moved most \textbf{Spellcasting} blocks into the \textbf{Actions} section, though whether you also do this is a matter of personal style.
+
+%% Manually toggle a bunch of internals to produce a modern stat block as an example.
+%% This will happen automatically if you use the |stats=modern| package option.
+
+\ExplSyntaxOn
+\let\DndMonster\DndMonsterModernBg
+\let\endDndMonster\endDndMonsterModernBg
+\bool_set_true:N \l__dnd_modern_stats_bool
+\ExplSyntaxOff
 
@@
 
-The |DndMonster| environment is used to typeset monster and NPC stat blocks. The module supplies many functions to easily typeset the contents of the stat block
+\ExplSyntaxOn
+\bool_set_false:N \l__dnd_modern_stats_bool
+\let\DndMonster\DndMonsterClassicBg
+\let\endDndMonster\endDndMonsterClassicBg
+\ExplSyntaxOff
 

### 2024-10-27 article.tex
Added spanning title in multi-column table example
Removed listparagraph with the simpler "description" environment as per sargeant (see commits https://github.com/sargeant/DND-5e-LaTeX-Template/commit/700737d4a58f9732a41e97a069d3f2d6aa70b96a and https://github.com/sargeant/DND-5e-LaTeX-Template/commit/c9fd42d9395711ee4934f0ecc820b6dd64c30693)

--- 2022-10-27 article.tex
@@
 \subsubsection{Hanging Indent Features}
-The |listparagraph| format allows hanging indented
+The |{description}| environment allows hanging indented
 lists of options, such as those used for class features,
@@
 
-\listparagraph[6pt]{Doors}
-{The doors are made from thick lumber and are unlocked.}
+\begin{description}
+  \item[Doors.]
+  The doors are made from thick lumber and are unlocked.
 
-\listparagraph{Light}
-{The area is illuminated by candles placed in sconces on the
+  \item[Light.]
+  The area is illuminated by candles placed in sconces on the
   walls. Each candle has had a \textit{continual flame} spell
   cast on it. Dispelling a flame is rumoured to give grievous offence
-to the host.}
+  to the host.
 
-\listparagraph{Ventilation}
-{All areas contain an adequate air supply. The air is renewed
-via lung-like sacks that cling to the ceiling.}
+  \item[Ventilation.]
+  All areas contain an adequate air supply. The air is renewed
+  via lung-like sacks that cling to the ceiling.
+\end{description}
 
@@
 \begin{multicols}{2}
-\begin{DndAltTable}[header=Encounters]{cX}
+\begin{DndAltTable}[header=Encounters~(With~Spanning~Title)]{cX}
 ...
@@
 \begin{multicols}{2}
-\begin{DndAltTable}[header=Encounters]{cX}
+\begin{DndAltTable}[header=Encounters~(With~Spanning~Title)]{cX}
     \textbf{d10} & \textbf{Encounter} \\

### 2024-10-27 example.tex
Removed listparagraph with the simpler "description" environment as per sargeant (see commits https://github.com/sargeant/DND-5e-LaTeX-Template/commit/700737d4a58f9732a41e97a069d3f2d6aa70b96a and https://github.com/sargeant/DND-5e-LaTeX-Template/commit/c9fd42d9395711ee4934f0ecc820b6dd64c30693)

--- 2022-12-21 example.tex
@@
 \subsubsection{Hanging Indent Features}
-The |\listparagraph| format allows hanging indented
+The |{description}| environment allows hanging indented
 lists of options, such as those used for class features,

### 2024-10-27 high-contrast-example.tex
Added spanning title in multi-column table example
Removed listparagraph from high-contrast-example.tex

--- 2022-10-27 example.tex
@@
-\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode]{dndbook}
+\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode,highcontrast]{dndbook}
 

### 2024-10-30 example.tex

@@
 \usetikzlibrary{intersections} % Required for ornamentedtabular
+\usepackage{wrapfig}
 
@@
 
-The module has three environments for setting text apart so that it is drawn to the reader's attention. |DndReadAloud| is used for text that a game master would read aloud.
+The module has several environments for setting text apart so that it is drawn to the reader's attention. |DndReadAloud| is used for text that a game master would read aloud.
 
@@
 \end{DndSidebar}
+
+You can represent an attached note (for example, for notes from Bigby or Mordenkainen) using the |DndAside| environment.
+
+\begin{DndAside}
+  This is the part where I give you a little extra information or make a witty comment to keep you entertained while you read.
+\end{DndAside}
+
+The |DndQuotation| environment goes a little further, offering the option of comment attribution, and tilts the note at a slight angle.
+
+\begin{DndQuotation}{The Author}
+  This is the part where I give you a little extra information or make a witty comment to keep you entertained while you read.
+\end{DndQuotation}
 
@@
       ]
-    % Traits
+
     \DndMonsterAction{Innate Spellcasting}
@@
 
-The stat block can be formatted either as a single column, or as a block that spans the page horizontally.
+When used with the |stats=modern| package option, some additional values are available for customization: |DndMonsterBasics| takes an |initiative| option to display as part of the initial block; it appears to the right of the \textbf{Armor Class} option.
+The |DndMonsterAbilityScores| command now has options for |str save|, |dex save|, etc, which if provided will replace the values in the appropriate \textbf{save} column of the abilities block.
+Lastly, modern stat blocks use an explicit section title for traits (the actions appearing between |DndMonsterDetails| and the \textbf{Actions} section).
+WotC also seems to have moved most \textbf{Spellcasting} blocks into the \textbf{Actions} section, though whether you also do this is a matter of personal style.
+
+%% Manually toggle a bunch of internals to produce a modern stat block as an example.
+%% This will happen automatically if you use the |stats=modern| package option.
+
+\ExplSyntaxOn
+\let\DndMonster\DndMonsterModernBg
+\let\endDndMonster\endDndMonsterModernBg
+\bool_set_true:N \l__dnd_modern_stats_bool
+\ExplSyntaxOff
+
+% Monster stat block
+\begin{DndMonster}[float*=b,width=\textwidth + 8pt]{Monster Foo}
+  \begin{multicols}{2}
+    \DndMonsterType{Medium aberration (metasyntactic variable), neutral evil}
+
+    % If you want to use commas in the key values, enclose the values in braces.
+    \DndMonsterBasics[
+        armor-class = {9 (12 with \emph{mage armor})},
+        hit-points  = {\DndDice{3d8 + 3}},
+        speed       = {30 ft., fly 30 ft.},
+        initiative  = --1,
+      ]
+
+    \DndMonsterAbilityScores[
+        str = 12,
+        dex = 8,
+        con = 13,
+        int = 10,
+        wis = 14,
+        cha = 15,
+      ]
+
+    \DndMonsterDetails[
+        %saving-throws = {Str +0, Dex +0, Con +0, Int +0, Wis +0, Cha +0},
+        %skills = {Acrobatics +0, Animal Handling +0, Arcana +0, Athletics +0, Deception +0, History +0, Insight +0, Intimidation +0, Investigation +0, Medicine +0, Nature +0, Perception +0, Performance +0, Persuasion +0, Religion +0, Sleight of Hand +0, Stealth +0, Survival +0},
+        %damage-vulnerabilities = {cold},
+        %damage-resistances = {bludgeoning, piercing, and slashing from nonmagical attacks},
+        %damage-immunities = {poison},
+        %condition-immunities = {poisoned},
+        senses = {darkvision 60 ft., passive Perception 10},
+        languages = {Common, Goblin, Undercommon},
+        challenge = 1,
+      ]
+
+    \DndMonsterSection{Traits}
+    \DndMonsterAction{Innate Spellcasting}
+    Foo's spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It can innately cast the following spells, requiring no material components:
+    \begin{DndMonsterSpells}
+      \DndInnateSpellLevel{misty step}
+      \DndInnateSpellLevel[3]{fog cloud, rope trick}
+      \DndInnateSpellLevel[1]{identify}
+    \end{DndMonsterSpells}
+
+    \DndMonsterAction{Spellcasting}
+    Foo is a 2nd-level spellcaster. Its spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It has the following sorcerer spells prepared:
+    \begin{DndMonsterSpells}
+      \DndMonsterSpellLevel{blade ward, fire bolt, light, shocking grasp}
+      \DndMonsterSpellLevel[1][3]{burning hands, mage armor, shield}
+    \end{DndMonsterSpells}
+
+    \DndMonsterSection{Actions}
+    \DndMonsterAction{Multiattack}
+    The foo makes two melee attacks.
+
+    %Default values are shown commented out
+    \DndMonsterAttack[
+      name=Dagger,
+      %distance=both, % valid options are in the set {both,melee,ranged},
+      %type=weapon, %valid options are in the set {weapon,spell}
+      mod=+3,
+      %reach=5,
+      %range=20/60,
+      %targets=one target,
+      dmg=\DndDice{1d4+1},
+      dmg-type=piercing,
+      %plus-dmg=,
+      %plus-dmg-type=,
+      %or-dmg=,
+      %or-dmg-when=,
+      %extra=,
+    ]
+
+    %\DndMonsterMelee calls \DndMonsterAttack with the melee option
+    \DndMonsterMelee[
+      name=Flame Tongue Longsword,
+      mod=+3,
+      %reach=5,
+      %targets=one target,
+      dmg=\DndDice{1d8+1},
+      dmg-type=slashing,
+      plus-dmg=\DndDice{2d6},
+      plus-dmg-type=fire,
+      or-dmg=\DndDice{1d10+1},
+      or-dmg-when=if used with two hands,
+      %extra=,
+    ]
+
+    %\DndMonsterRanged calls \DndMonsterAttack with the ranged option
+    \DndMonsterRanged[
+      name=Assassin's Light Crossbow,
+      mod=+1,
+      range=80/320,
+      dmg=\DndDice{1d8},
+      dmg-type=piercing,
+      %plus-dmg=,
+      %plus-dmg-type=,
+      %or-dmg=,
+      %or-dmg-when=,
+      extra={, and the target must make a DC 15 Constitution saving throw, taking 24 (7d6) poison damage on a failed save, or half as much damage on a successful one}
+    ]
+
+    % Legendary Actions
+    \DndMonsterSection{Legendary Actions}
+    The foo can take 3 legendary actions, choosing from the options below.
+Only one legendary action option can be used at a time and only at the end of another creature's turn.
+The foo regains spent legendary actions at the start of its turn.
+
+    \begin{DndMonsterLegendaryActions}
+      \DndMonsterLegendaryAction{Move}{The foo moves up to its speed.}
+      \DndMonsterLegendaryAction{Dagger Attack}{The foo makes a dagger attack.}
+      \DndMonsterLegendaryAction{Create Contract (Costs 3 Actions)}{The foo presents a contract in a language it knows and waves it in the face of a creature within 10 feet.
+The creature must make a DC 10 Intelligence saving throw.
+On a failure, the creature is incapacitated until the start of the foo's next turn.
+A creature who cannot read the language in which the contract is written has advantage on this saving throw.}
+    \end{DndMonsterLegendaryActions}
+  \end{multicols}
+\end{DndMonster}
+
+\ExplSyntaxOn
+\bool_set_false:N \l__dnd_modern_stats_bool
+\let\DndMonster\DndMonsterClassicBg
+\let\endDndMonster\endDndMonsterClassicBg
+\ExplSyntaxOff
 

### 2024-10-30 article.tex
Added Aside/Quotation to other examples; fixed layout issues with Aside/Quotation and table styles

@@
 It does not break over columns and is best used with a figure environment to float it to one corner of the page where the surrounding text can then flow around it.
+
+  Use the |\tocside{title}| command to create an entry in the table of contents, if you want.
 \end{DndSidebar}
+
+You can represent an attached note (for example, for notes from Bigby or Mordenkainen) using the |DndAside| environment.
+
+\begin{DndAside}
+  This is the part where I give you a little extra information or make a witty comment to keep you entertained while you read.
+\end{DndAside}
+
+The |DndQuotation| environment goes a little further, offering the option of comment attribution, and tilts the note at a slight angle.
+
+\begin{DndQuotation}{The Author}
+  This is the part where I give you a little extra information or make a witty comment to keep you entertained while you read.
+\end{DndQuotation}
 

### 2024-10-30 example.tex
Added Aside/Quotation to other examples; fixed layout issues with Aside/Quotation and table styles

@@
 
-\section{Tables}
-
-\subsection{Regular Table}
+\chapter{Tables}
+
+\section{Regular Table}
 The |DndTable| colors the even rows and is set to the width of a line by default.
@@
 
-\subsection{Alternate Table Background}
+\section{Alternate Table Background}
 
@@
 
-\subsection{Split Tables}
+\section{Split Tables}
 Temporarily adding a column using |multicols| can
@@
 
+%\newcolumn
 This achieves the following effect:
@@
 
-\subsection{Long Table that Spans Pages}
+\section{Long Table that Spans Pages}
 
@@
 
-\subsection{Tables with Footnotes}
+\newcolumn
+\section{Tables with Footnotes}
 Surrounding one of the existing table types with a |minipage| section
@@
 
-\subsection{Ornamented Tables}
+\section{Ornamented Tables}
 The |ornamentedtabular| allows tables similar to those used for spellcasters

### 2024-10-30 fancy-example.tex
Added Aside/Quotation to other examples; fixed layout issues with Aside/Quotation and table styles

@@
 
-\section{Tables}
+You can represent an attached note (for example, for notes from Bigby or Mordenkainen) using the |DndAside| environment.
 
-\subsection{Regular Table}
+\begin{DndAside}
+  This is the part where I give you a little extra information or make a witty comment to keep you entertained while you read.
+\end{DndAside}
+
+The |DndQuotation| environment goes a little further, offering the option of comment attribution, and tilts the note at a slight angle.
+
+\begin{DndQuotation}{The Author}
+  This is the part where I give you a little extra information or make a witty comment to keep you entertained while you read.
+\end{DndQuotation}
+
+\chapter{Tables}
+
+\section{Regular Table}
 The |DndTable| colors the even rows and is set to the width of a line by default.
@@
 
-\subsection{Tables with Footnotes}
+\section{Tables with Footnotes}
 Surrounding one of the existing table types with a |minipage| section
